### 2025-01-07 paper/main.tex
paper directory

\documentclass[sigconf]{acmart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}
%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation email}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/2018/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{BugsInDLLs: A Database of Bugs in Deep Learning Libraries to
  Enable the Evaluation of Testing Techniques}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
%% \author{Ben Trovato}
%% \authornote{Both authors contributed equally to this research.}
%% \email{trovato@corporation.com}
%% \orcid{1234-5678-9012}
%% \author{G.K.M. Tobin}
%% \authornotemark[1]
%% \email{webmaster@marysville-ohio.com}
%% \affiliation{%
%%   \institution{Institute for Clarity in Documentation}
%%   \city{Dublin}
%%   \state{Ohio}
%%   \country{USA}
%% }

%% \author{Lars Th{\o}rv{\"a}ld}
%% \affiliation{%
%%   \institution{The Th{\o}rv{\"a}ld Group}
%%   \city{Hekla}
%%   \country{Iceland}}
%% \email{larst@affiliation.org}

\author{M. M. Abid Naziri}
\affiliation{%
  \institution{NC State University}
  %\city{Rocquencourt}
  \country{USA}
}
\email{mnaziri@ncsu.edu}

\author{Feiran Qin}
\affiliation{%
 \institution{NC State University}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{USA}}
\email{fqin2@ncsu.edu}

\author{Aman Kumar Singh}
\affiliation{%
 \institution{?}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{?}}
\email{?}

\author{Saikat Dutta}
\affiliation{%
 \institution{Cornell University}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{USA}}
\email{saikatd@cornell.edu}

\author{Marcelo d'Amorim}
\affiliation{%
 \institution{NC State University}
 %% \city{Doimukh}
 %% \state{Arunachal Pradesh}
 \country{USA}}
\email{mdamori@ncsu.edu}

%% \author{Julius P. Kumquat}
%% \affiliation{%
%%   \institution{The Kumquat Consortium}
%%   \city{New York}
%%   \country{USA}}
%% \email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>00000000.0000000.0000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}
%% %% A "teaser" image appears between the author and affiliation
%% %% information and the body of the document, and typically spans the
%% %% page.
%% \begin{teaserfigure}
%%   \includegraphics[width=\textwidth]{sampleteaser}
%%   \caption{Seattle Mariners at Spring Training, 2010.}
%%   \Description{Enjoying the baseball game from the third-base
%%   seats. Ichiro Suzuki preparing to bat.}
%%   \label{fig:teaser}
%% \end{teaserfigure}

%% \received{20 February 2007}
%% \received[revised]{12 March 2009}
%% \received[accepted]{5 June 2009}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
%% \begin{acks}
%% To Robert, for the bagels and explaining CMYK and color spaces.
%% \end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2025-01-08 paper/main.tex
first pass on abstract

@@
 
+%% macros
+\newcommand{\tname}{BugsInDLLs}
+\newcommand{\jax}{JAX}
+\newcommand{\torch}{PyTorch}
+\newcommand{\tf}{Tensorflow}
+\newcommand{\numbugs}{115}
+
 %%
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{BugsInDLLs: A Database of Bugs in Deep Learning Libraries to
+\title{\tname: A Database of Bugs in Deep Learning Libraries to
   Enable the Evaluation of Testing Techniques}
@@
 
+\author{Aman Kumar Singh}
+\affiliation{%
+ \institution{?}
+ %% \city{Doimukh}
+ %% \state{Arunachal Pradesh}
+ \country{?}}
+\email{?}
+
 \author{Feiran Qin}
@@
 \email{fqin2@ncsu.edu}
-
-\author{Aman Kumar Singh}
-\affiliation{%
- \institution{?}
- %% \city{Doimukh}
- %% \state{Arunachal Pradesh}
- \country{?}}
-\email{?}
 
@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+  \sloppy
+  AI-enabled applications are prolific today. Deep Learning
+  libraries~(DLL), such as \torch{} and \tf{}, provide the building
+  blocks for the AI components of these applications. As any piece of
+  software, these libraries can be buggy.
+  %% and those bugs can affect a
+  %% great deal of applications using those libraries.
+  An impressive number of techniques have been recently proposed to
+  find those bugs, but the lack of curated set of reproducible bugs
+  hinders credible evaluation of those techniques. We present \tname,
+  a database of curated reproducible bugs to fill that gap.
+  %% enable credible  evaluation of bug-finding DLL testing techniques.
+  Our dataset currently consists of \numbugs{} environments to
+  reproduce bugs across three popular DLL libraries, namely, \jax,
+  \tf, and \torch.
 \end{abstract}
@@
 %%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>00000000.0000000.0000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
+%% \begin{CCSXML}
+%% <ccs2012>
+%%  <concept>
+%%   <concept_id>00000000.0000000.0000000</concept_id>
+%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%%   <concept_significance>500</concept_significance>
+%%  </concept>
+%%  <concept>
+%%   <concept_id>00000000.00000000.00000000</concept_id>
+%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%%   <concept_significance>300</concept_significance>
+%%  </concept>
+%%  <concept>
+%%   <concept_id>00000000.00000000.00000000</concept_id>
+%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%%   <concept_significance>100</concept_significance>
+%%  </concept>
+%%  <concept>
+%%   <concept_id>00000000.00000000.00000000</concept_id>
+%%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%%   <concept_significance>100</concept_significance>
+%%  </concept>
+%% </ccs2012>
+%% \end{CCSXML}
 
-\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+%% \ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+%% \ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+%% \ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+%% \ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
-  Your, Paper}
+\keywords{Deep learning libraries, testing, benchmarking}
 %% %% A "teaser" image appears between the author and affiliation
@@
 \section{Introduction}
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-%% \begin{acks}
-%% To Robert, for the bagels and explaining CMYK and color spaces.
-%% \end{acks}
 
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
 \bibliographystyle{ACM-Reference-Format}

### 2025-01-08 paper/main.tex
first pass on abstract
changing author ordering
title change as per Saikat's recommendation
minor changes to abstract

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{\tname: A Database of Bugs in Deep Learning Libraries to
-  Enable the Evaluation of Testing Techniques}
+\title{\tname: A Database of Reproducible Bugs in Deep
+  Learning Libraries to Enable Systematic Evaluation of Testing
+  Techniques}
 
@@
 
+\author{Benjamin Wu}
+\affiliation{%
+ \institution{?}
+ %% \city{Doimukh}
+ %% \state{Arunachal Pradesh}
+ \country{?}}
+\email{?}
+
 \author{Saikat Dutta}
@@
   AI-enabled applications are prolific today. Deep Learning
-  libraries~(DLL), such as \torch{} and \tf{}, provide the building
+  libraries~(DLLs), such as \torch{} and \tf{}, provide the building
   blocks for the AI components of these applications. As any piece of
@@
   An impressive number of techniques have been recently proposed to
-  find those bugs, but the lack of curated set of reproducible bugs
-  hinders credible evaluation of those techniques. We present \tname,
+  find those bugs, but the lack of a curated set of reproducible bugs
+  in DLLs hinders credible evaluation of testing techniques. We present \tname,
   a database of curated reproducible bugs to fill that gap.

### 2025-01-08 paper/main.tex
minor change to abstract

@@
   %% great deal of applications using those libraries.
-  An impressive number of techniques have been recently proposed to
-  find those bugs, but the lack of a curated set of reproducible bugs
-  in DLLs hinders credible evaluation of testing techniques. We present \tname,
-  a database of curated reproducible bugs to fill that gap.
+  An impressive number of bug-finding techniques to address this
+  problem, but the lack of a curated set of reproducible bugs in DLLs
+  hinders credible evaluation of such techniques. We present \tname, a
+  database of curated reproducible bugs to fill that gap.
   %% enable credible  evaluation of bug-finding DLL testing techniques.

### 2025-01-08 paper/main.tex
aman's institution
adding totals table
adding material that abid provided

@@
 \documentclass[sigconf]{acmart}
+
+\usepackage{multirow}
 %%
@@
 \affiliation{%
- \institution{?}
+ \institution{Amrita Vishwa Vidyapeetham}
  %% \city{Doimukh}
  %% \state{Arunachal Pradesh}
- \country{?}}
-\email{?}
+ \country{India}}
+\email{amanks@am.amrita.edu}
 
@@
 \affiliation{%
- \institution{?}
+ \institution{Purdue University}
  %% \city{Doimukh}
  %% \state{Arunachal Pradesh}
- \country{?}}
-\email{?}
+ \country{USA}}
+\email{wu2059@purdue.edu}
 
@@
 
+Challenges...
+
+\begin{enumerate}
+
+\sloppy  
+\item \textbf{Handling bugs from nighly builds require saving wheels.}
+  Many of the reproducible bugs rely on nightly builds since they can
+  not be reproduced with any release builds. These nightly builds have
+  a limited amount of time when they are publicly available, and they
+  are de-indexed and removed after that time. In order to ensure bugs
+  that depend on these nightly builds can be reproduced after these
+  builds disappear, we save the whl files of these builds.
+
+\item \textbf{Handling bugs in specific GPU-CUDA versions require OS
+  changes:} Many of the GPU-related bugs can only be repro
+  duced with
+  specific GPU builds and specific CUDA builds. Changing different
+  virtual environments does not change the CUDA versions of the
+  system. That is why we use Docker when a bug relies on a specific
+  version of CUDA to be installed in the system.
+
+\end{enumerate}
+
+Table~\ref{...}
+
+\begin{table}
+  \centering
+  \caption{Characterization of reproducible bugs from \tname.}
+\begin{tabular}{lrrr}
+  \toprule
+  & \multirow{2}{*}{\#} &  \multicolumn{1}{c}{build}          &   \multicolumn{1}{c}{enviroment}  \\
+  &   & release-nightly &  venv-docker  \\
+  \cmidrule(lr){2-4}
+  \jax{} & 44 & 43-1 &  43-1 \\
+  \torch{} & 33 & 15-18 & 19-14 \\
+  \tf{} & 25 & 24-1 & 25-0 \\
+  \midrule
+  \multicolumn{1}{c}{$\Sigma$} & 102 & 82-20 & 87-15 \\
+  \bottomrule
+\end{tabular}
+\end{table}
+
 \bibliographystyle{ACM-Reference-Format}

### 2025-01-09 paper/main.tex
u

@@
 \usepackage{multirow}
+\usepackage{xcolor}
 %%
@@
 %% macros
+\newcommand{\Fix}[1]{\textbf{[[}\textcolor{red}{#1}\textbf{]]}}
 \newcommand{\tname}{BugsInDLLs}
@@
 
-Challenges...
+\sloppy Serveral important application domains (e.g., transportation,
+medical diagnosis, software development) use AI to optimize some
+element of their business process. Deep Learning libraries~(DLLs)
+(e.g., \jax, \torch{}, and \tf{}) provide the building blocks for the
+AI components of these applications.  Unfortunately, as any piece of
+software, these libraries contain bugs. An impressive number of
+techniques have been recently proposed to find bugs in these
+libraries~\Fix{cite 10+ fuzzing papers here}, however we observe that
+the evaluation of these techniques do \emph{not} use a reference set
+of reproducible bugs to evaluate their effectiveness. The lack of
+evaluation standards is an obstacle to evaluate progress in this
+important field.
+
+This paper presents \tname, a database of curated reproducible bugs to
+enable credible evaluation of DLL testing techniques.  Our dataset
+currently consists of \numbugs{} environments to reproduce bugs across
+three popular DLL libraries, namely, \jax, \tf, and \torch.
+
+\Fix{...}
 
@@
 
+\section{Methodology}
+\subsection{DLL and Bug Selection}
+\subsection{Reproducing Bugs}
+\subsection{}
+
+\section{\tname: Database of Bugs in DLLs}
+\subsection{Bug Interface}
+\subsection{Test Oracle}
+\subsection{Usage and Setup}
+
+\section{\tname: Use cases}
+
+\subsection{Evaluating DLL testing techniques}
+\subsection{Fault Detection}
+\subsection{Program Repair}
+
+\section{Related Work}
+
+\section{Conclusion and Future Work}
+
 \bibliographystyle{ACM-Reference-Format}

### 2025-01-09 paper/main.tex
updating macro numbugs

@@
 \newcommand{\tf}{Tensorflow}
-\newcommand{\numbugs}{115}
+\newcommand{\numbugs}{102}
 
@@
   An impressive number of bug-finding techniques to address this
-  problem, but the lack of a curated set of reproducible bugs in DLLs
-  hinders credible evaluation of such techniques. We present \tname, a
-  database of curated reproducible bugs to fill that gap.
+  problem have been proposed, but the lack of a curated set of
+  reproducible bugs in DLLs hinders credible evaluation of these
+  techniques. We present \tname, a database of curated reproducible
+  bugs to fill that gap.
   %% enable credible  evaluation of bug-finding DLL testing techniques.
@@
   \midrule
-  \multicolumn{1}{c}{$\Sigma$} & 102 & 82-20 & 87-15 \\
+  \multicolumn{1}{c}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
   \bottomrule

### 2025-01-09 paper/main.tex
minor changes on organization

@@
 \sloppy Serveral important application domains (e.g., transportation,
-medical diagnosis, software development) use AI to optimize some
-element of their business process. Deep Learning libraries~(DLLs)
-(e.g., \jax, \torch{}, and \tf{}) provide the building blocks for the
-AI components of these applications.  Unfortunately, as any piece of
-software, these libraries contain bugs. An impressive number of
-techniques have been recently proposed to find bugs in these
-libraries~\Fix{cite 10+ fuzzing papers here}, however we observe that
-the evaluation of these techniques do \emph{not} use a reference set
-of reproducible bugs to evaluate their effectiveness. The lack of
-evaluation standards is an obstacle to evaluate progress in this
-important field.
+medicine, etc.) use AI to optimize some element of their business
+process. Deep Learning libraries~(DLLs), such as \jax, \torch{}, and
+\tf{}, provide the building blocks for the AI components of these
+applications.  Unfortunately, as any piece of software, these
+libraries contain bugs. An impressive number of techniques have been
+recently proposed to find bugs in these libraries~\Fix{cite 10+
+  fuzzing papers here}, however we observe that the evaluation of
+these techniques do \emph{not} use a reference set of reproducible
+bugs to evaluate their effectiveness. The lack of evaluation standards
+is an obstacle to the fair comparison of techniques, hindering
+research progress.
 
 This paper presents \tname, a database of curated reproducible bugs to
-enable credible evaluation of DLL testing techniques.  Our dataset
-currently consists of \numbugs{} environments to reproduce bugs across
-three popular DLL libraries, namely, \jax, \tf, and \torch.
+enable credible evaluation of DLL testing techniques. \tname\ is
+equiped with a command-line interface to enable researchers to analyze
+and reproduce bug instances.
 
-\Fix{...}
-
-\begin{enumerate}
-
-\sloppy  
-\item \textbf{Handling bugs from nighly builds require saving wheels.}
-  Many of the reproducible bugs rely on nightly builds since they can
-  not be reproduced with any release builds. These nightly builds have
-  a limited amount of time when they are publicly available, and they
-  are de-indexed and removed after that time. In order to ensure bugs
-  that depend on these nightly builds can be reproduced after these
-  builds disappear, we save the whl files of these builds.
-
-\item \textbf{Handling bugs in specific GPU-CUDA versions require OS
-  changes:} Many of the GPU-related bugs can only be repro
-  duced with
-  specific GPU builds and specific CUDA builds. Changing different
-  virtual environments does not change the CUDA versions of the
-  system. That is why we use Docker when a bug relies on a specific
-  version of CUDA to be installed in the system.
-
-\end{enumerate}
-
-Table~\ref{...}
+\section{Methodology}
 
@@
   \centering
+  \label{table:bug-characterization}
   \caption{Characterization of reproducible bugs from \tname.}
@@
 
-\section{Methodology}
-\subsection{DLL and Bug Selection}
-\subsection{Reproducing Bugs}
-\subsection{}
+Our dataset currently consists of \numbugs{} instances of reproducible
+bugs representing three popular DLL libraries, namely, \jax, \tf, and
+\torch. Table~\ref{table:bug-characterization} shows the list of bug
+instances for each supported library. Column ``\#'' shows the number
+of bug instances, column ``build'' shows the breakdown of bug
+instances based on releases of the library against those based on
+nightly builds, and column ``environment'' shows the breakdown of bug
+instances that use Python's virtual environment against those that run
+on a Docker container.
+
+\subsection{Selection of Libraries}
+
+\Fix{Abid, explain the rationale for selecting jax, torch, and tf.}
+
+\subsection{Selection of Bugs}
+
+\Fix{Abid, explain the selection criterion for the bugs.}
+
+\subsection{Challenges in Bug Reproduction}
+
+\textbf{Handling bugs from nighly builds require saving wheels.}  Many
+of the reproducible bugs rely on nightly builds since they can not be
+reproduced with any release builds. These nightly builds have a
+limited amount of time when they are publicly available, and they are
+de-indexed and removed after that time. In order to ensure bugs that
+depend on these nightly builds can be reproduced after these builds
+disappear, we save the whl files of these builds.
+
+\textbf{Handling bugs in specific GPU-CUDA versions require OS
+  changes:} Many of the GPU-related bugs can only be repro duced with
+specific GPU builds and specific CUDA builds. Changing different
+virtual environments does not change the CUDA versions of the
+system. That is why we use Docker when a bug relies on a specific
+version of CUDA to be installed in the system.
+
+\subsection{Method}
+
+\Fix{Abid, explain the method we used to create a bug instance}
 

### 2025-01-09 paper/main.tex
u

@@
 
-%% macros
-\newcommand{\Fix}[1]{\textbf{[[}\textcolor{red}{#1}\textbf{]]}}
-\newcommand{\tname}{BugsInDLLs}
-\newcommand{\jax}{JAX}
-\newcommand{\torch}{PyTorch}
-\newcommand{\tf}{Tensorflow}
-\newcommand{\numbugs}{102}
+\input{macros}
 
@@
   \caption{Characterization of reproducible bugs from \tname.}
-\begin{tabular}{lrrr}
+\begin{tabular}{l|rrr}
   \toprule
-  & \multirow{2}{*}{\#} &  \multicolumn{1}{c}{build}          &   \multicolumn{1}{c}{enviroment}  \\
+  & \multirow{2}{*}{\#} &  \multicolumn{1}{r}{build}          &   \multicolumn{1}{r}{enviroment}  \\
   &   & release-nightly &  venv-docker  \\
@@
   \midrule
-  \multicolumn{1}{c}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
+  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
   \bottomrule
@@
 \section{Related Work} 
+Defects4J\cite{just2014defects4j}
+BugsInPy~\cite{widyasari2020bugsinpy}
+Tests4Py~\cite{smytzek2024tests4py}
+Denchmark~\cite{kim2021denchmark}
 

### 2025-01-10 framework/stats.py
Initial integration for freefuzz

@@ -39,6 +39,7 @@ class Trie(object):
 #####################################
 
 def process_file(libname, print_fmt, total_bugs):
+    initial_bugs = total_bugs
     tr = Trie()
     print('----------------------------')
     print(libname)
@@ -56,6 +57,8 @@ def process_file(libname, print_fmt, total_bugs):
         num_c = 0
         num_py = 0      
         num_cuda = 0  
+        ##
+        num_nightly = 0
         for row in csv_reader:
             if row["Reproduced"] == "Yes":
                 total_bugs += 1
@@ -64,6 +67,8 @@ def process_file(libname, print_fmt, total_bugs):
                 
                 ## bug types
                 bug_m_type = row["Type"].strip().lower()
+                if bug_m_type == "":
+                    print(f"\nWARNING: {row['Issue #']} does not have a type")
                 if bug_m_type not in bug_manifest_type:
                     bug_manifest_type[bug_m_type] = 1
                 else:
@@ -71,10 +76,12 @@ def process_file(libname, print_fmt, total_bugs):
 
                 ## cpu/gpu
                 device = row["Device"].strip()
-                if device == "CPU":
+                if device.lower() == "cpu":
                     num_cpus += 1
-                elif device == "GPU":
+                elif device.lower() == "gpu":
                     num_gpus += 1
+                else:
+                    print(f"\nWARNING: {row['Issue #']} has this as the device: {device}\n")
                 
                 if row["Buggy File(s)"] > "":
                     for file in row["Buggy File(s)"].split(","):
@@ -88,17 +95,26 @@ def process_file(libname, print_fmt, total_bugs):
                             num_c += 1
                         elif ".py" in file or ".pyi" in file:
                             num_py += 1                        
+                
+                if row["Nightly"].lower().strip() == "yes":
+                    num_nightly += 1
 
+        print(f'  # Total: {total_bugs - initial_bugs}')
         print(f'  # Require GPU: {num_gpus} ({num_gpus*100/(num_gpus+num_cpus):.2f}%)')
         print(f'  # Do NOT Require GPU: {num_cpus} ({num_cpus*100/(num_gpus+num_cpus):.2f}%)')        
         print(f'  # C/CPP: {num_c} ({num_c*100/(num_c+num_py+num_cuda):.2f}%)')
[…]

### 2025-01-10 tool-integration/FreeFuzz/install_freefuzz_docker.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+git clone https://github.com/ise-uiuc/FreeFuzz.git
+docker build -t freefuzz .
+docker run --name freefuzz -d freefuzz:latest
+docker exec -it freefuzz mongorestore dump/

### 2025-01-10 tool-integration/FreeFuzz/run_freefuzz_docker.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+
+libname=${1:-torch}
+
+if [[ "$libname" == "torch" ]]; then
+    docker exec -it freefuzz bash -c "cd src && python3 FreeFuzz.py --conf demo_torch.conf"
+elif [[ "$libname" == "tensorflow" ]]; then
+    docker exec -it freefuzz bash -c "cd src && python3 FreeFuzz.py --conf demo_tf.conf"
+else
+    echo "$libname not supported"
+fi

### 2025-01-10 tool-integration/FreeFuzz/install_freefuzz_docker.sh
Implemented the tool integration

@@ -2,5 +2,5 @@
 
 git clone https://github.com/ise-uiuc/FreeFuzz.git
 docker build -t freefuzz .
-docker run --name freefuzz -d freefuzz:latest
+docker run --name freefuzz --gpus all -d freefuzz:latest
 docker exec -it freefuzz mongorestore dump/

### 2025-01-10 tool-integration/FreeFuzz/run_freefuzz_docker.sh

@@ -2,9 +2,9 @@
 
 libname=${1:-torch}
 
-if [[ "$libname" == "torch" ]]; then
+if [[ "$libname" == "torch" ]] || [[ "$libname" == "pytorch" ]]; then
     docker exec -it freefuzz bash -c "cd src && python3 FreeFuzz.py --conf demo_torch.conf"
-elif [[ "$libname" == "tensorflow" ]]; then
+elif [[ "$libname" == "tensorflow" ]] || [[ "$libname" == "tf" ]]; then
     docker exec -it freefuzz bash -c "cd src && python3 FreeFuzz.py --conf demo_tf.conf"
 else
     echo "$libname not supported"

### 2025-01-11 paper/main.tex
Added citations for fuzzing tools

@@
   \sloppy
-  AI-enabled applications are prolific today. Deep Learning
-  libraries~(DLLs), such as \torch{} and \tf{}, provide the building
+  AI-enabled applications are prolific today. Deep Learning~(DL)
+  libraries, such as \torch{} and \tf{}, provide the building
   blocks for the AI components of these applications. As any piece of
@@
   problem have been proposed, but the lack of a curated set of
-  reproducible bugs in DLLs hinders credible evaluation of these
+  reproducible bugs in DL libraries hinders credible evaluation of these
   techniques. We present \tname, a database of curated reproducible
   bugs to fill that gap.
-  %% enable credible  evaluation of bug-finding DLL testing techniques.
+  %% enable credible  evaluation of bug-finding DL library testing techniques.
   Our dataset currently consists of \numbugs{} environments to
-  reproduce bugs across three popular DLL libraries, namely, \jax,
+  reproduce bugs across three popular DL libraries, namely, \jax,
   \tf, and \torch.
@@
 medicine, etc.) use AI to optimize some element of their business
-process. Deep Learning libraries~(DLLs), such as \jax, \torch{}, and
+process. Deep Learning~(DL) libraries, such as \jax, \torch{}, and
 \tf{}, provide the building blocks for the AI components of these
@@
 libraries contain bugs. An impressive number of techniques have been
-recently proposed to find bugs in these libraries~\Fix{cite 10+
-  fuzzing papers here}, however we observe that the evaluation of
+recently proposed to find bugs in these libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
+however we observe that the evaluation of
 these techniques do \emph{not} use a reference set of reproducible
@@
 This paper presents \tname, a database of curated reproducible bugs to
-enable credible evaluation of DLL testing techniques. \tname\ is
-equiped with a command-line interface to enable researchers to analyze
+enable credible evaluation of DL library testing techniques. \tname\ is
+equipped with a command-line interface to enable researchers to analyze
 and reproduce bug instances.
@@
 Our dataset currently consists of \numbugs{} instances of reproducible
-bugs representing three popular DLL libraries, namely, \jax, \tf, and
+bugs representing three popular DL libraries, namely, \jax, \tf, and
 \torch. Table~\ref{table:bug-characterization} shows the list of bug
@@
 
-\section{\tname: Database of Bugs in DLLs}
+\section{\tname: Database of Bugs in DL libraries}
 \subsection{Bug Interface}
@@
 
-\subsection{Evaluating DLL testing techniques}
+\subsection{Evaluating DL library testing techniques}
 \subsection{Fault Detection}

### 2025-01-11 paper/main.tex
pass

@@
 
-\section{Methodology}
+\section{Objects and Methods}
 
@@
   \centering
-  \label{table:bug-characterization}
-  \caption{Characterization of reproducible bugs from \tname.}
+  \caption{\label{table:bug-characterization}Characterization of reproducible bugs from \tname.}
 \begin{tabular}{l|rrr}
-  \toprule
-  & \multirow{2}{*}{\#} &  \multicolumn{1}{r}{build}          &   \multicolumn{1}{r}{enviroment}  \\
-  &   & release-nightly &  venv-docker  \\
-  \cmidrule(lr){2-4}
-  \jax{} & 44 & 43-1 &  43-1 \\
-  \torch{} & 33 & 15-18 & 19-14 \\
-  \tf{} & 25 & 24-1 & 25-0 \\
-  \midrule
-  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
-  \bottomrule
+  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
+  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
+  \\ \cmidrule(lr){2-4} \jax{} & 44 & 43-1 & 43-1 \\ \torch{} & 33 &
+  15-18 & 19-14 \\ \tf{} & 25 & 24-1 & 25-0 \\ \midrule
+  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15
+  \\ \bottomrule
 \end{tabular}
@@
 
-Our dataset currently consists of \numbugs{} instances of reproducible
-bugs representing three popular DL libraries, namely, \jax, \tf, and
+This section describes the criteria for selecting libraries and bugs
+(Section~\ref{sec:selection-criterion}), the challenges for bug
+reproduction (Section~\ref{sec:challenges}), and the method we
+followed to create bug instances (Section~\ref{sec:method}). The
+\tname\ database consists of \numbugs{} instances of reproducible bugs
+representing three popular DL libraries, namely, \jax, \tf, and
 \torch. Table~\ref{table:bug-characterization} shows the list of bug
@@
 
-\subsection{Selection of Libraries}
+\subsection{Selection Criterion}
+\label{sec:selection-criterion}
 
@@
 
-\subsection{Selection of Bugs}
+\Fix{Abid, explain the criterion for selecting the bugs (e.g., it
+  contains test code showing the problem).}
 
-\Fix{Abid, explain the selection criterion for the bugs.}
+\subsection{Challenges}
+\label{sec:challenges}
 
-\subsection{Challenges in Bug Reproduction}
+\textbf{Handling bugs from nighly builds requires saving wheels.}  Many
+of the reproducible bugs rely on nightly builds of the
+libraries. These builds are available for a limited amount of time. In
+order to ensure bugs reported on these builds to remain reproducible,
+it is imperative to save wheel files~\cite{wheels} for the
+correspondind builds.
 
-\textbf{Handling bugs from nighly builds require saving wheels.}  Many
-of the reproducible bugs rely on nightly builds since they can not be
-reproduced with any release builds. These nightly builds have a
-limited amount of time when they are publicly available, and they are
-de-indexed and removed after that time. In order to ensure bugs that
-depend on these nightly builds can be reproduced after these builds
-disappear, we save the whl files of these builds.
-
-\textbf{Handling bugs in specific GPU-CUDA versions require OS
+\textbf{Handling bugs in specific GPU-CUDA versions requires OS
   changes:} Many of the GPU-related bugs can only be repro duced with
-specific GPU builds and specific CUDA builds. Changing different
-virtual environments does not change the CUDA versions of the
+specific GPU builds\Fix{I don't understance GPU builds. do you mean
+  GPU vendor/version? give example} and specific CUDA builds. Changing
+different virtual environments does not change the CUDA
+versions\Fix{Do you mean ``it is not possible to change the CUDA (or
+  GPU) version with Python's virtual environments''?} of the
 system. That is why we use Docker when a bug relies on a specific
@@
 \subsection{Method}
+\label{sec:method}
 
-\Fix{Abid, explain the method we used to create a bug instance}
+\Fix{Abid, explain the steps you followed to create a bug
+  isntance. For example, (1) selected an issues (according to the
+  criteria defined in 2.1), (2) ...}
 
@@
 \subsection{Bug Interface}
+
+\begin{table}
+  \centering
+  \caption{\label{table:bug-interface}\tname's bug interface.}
+\begin{tabular}{lp{6.5cm}}
+\toprule
+list-tests & List the tests available on this dataset\\
+run-test & Runs one test\\
+run-tests & Runs all the tests\\
+show-info & Shows information about the tests available on this benchmark\\
+stats & Shows statistics about this dataset (e.g., number of tests
+that require GPU, number of tests that reproduce bugs in C or Python
+code, etc.)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Table~\ref{table:bug-interface} shows \Fix{...}
+
 \subsection{Test Oracle}
+
+\Fix{explain that the test passes if the bug can be reproduced}
+
 \subsection{Usage and Setup}
+
+\subsubsection{Running one bug instance}
+
+\Fix{walkthrough an example. Show input and part of output. Explain
+  the output.}
+
+\subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}
+
+\Fix{walkthrough an example. Show input and part of output. Explain
+  the output.}
 

### 2025-01-11 paper/main.tex
Added selection criterion

@@
 
-\Fix{Abid, explain the rationale for selecting jax, torch, and tf.}
+% \Fix{Abid, explain the rationale for selecting jax, torch, and tf.}
 
-\Fix{Abid, explain the criterion for selecting the bugs (e.g., it
-  contains test code showing the problem).}
+Amongst many DL libraries, the most popular libraries for developing AI-enabled applications and used in testing tools are \torch~and \tf.
+\jax~is a relatively newer entry to the list of libraries but it is rapidly gaining popularity as well.
+All three of these libraries are open source with active communities that support the libraries, making them very suitable for developing testing tools around.
+We chose these three popular datasets in order to enhance the process of developing testing tools around these libraries.
+
+% \Fix{Abid, explain the criterion for selecting the bugs (e.g., it
+  % contains test code showing the problem).}
+
+For the bugs from these libraries, we focused on bug reports that have been accepted by the developer community as true bugs.
+We determine this by checking whether the bugs have appropriate labels and have been fixed with pull requests linked to them.
+Among these confirmed bug reports, we choose the ones that have enough information to reproduce the bugs i.e.
+code to reproduce the bug, enviroment required for reproduction, clear description of desired behavior etc.
+Once we can successfully reproduce the bug by creating the enviroment detailed in the report, we choose the bug to be included in our dataset.
+
+\Fix{Please review and revise}
 

### 2025-01-11 pytorch/issue_121072/reproduce_bug.sh
fix: update reproduce_bug.sh for PyTorch issue #121072 to remove Docker image and clear build cache after use

@@ -45,4 +45,6 @@ fi
 
 docker build -t issue_121072 .
 docker run -it --rm --gpus all issue_121072
+docker rmi -f issue_121072
+docker system prune -f
 exit $?

### 2025-01-11 paper/main.tex
Addressed some comments

@@
 \textbf{Handling bugs in specific GPU-CUDA versions requires OS
-  changes:} Many of the GPU-related bugs can only be repro duced with
-specific GPU builds\Fix{I don't understance GPU builds. do you mean
-  GPU vendor/version? give example} and specific CUDA builds. Changing
-different virtual environments does not change the CUDA
-versions\Fix{Do you mean ``it is not possible to change the CUDA (or
-  GPU) version with Python's virtual environments''?} of the
-system. That is why we use Docker when a bug relies on a specific
-version of CUDA to be installed in the system.
+  changes:} Many of the GPU-related bugs can only be reproduced with
+library versions that are built with specific versions of CUDA.
+These builds require those specific CUDA drivers to be installed on
+the system, and the version of the CUDA driver installed on a system
+can not be changed with Python's virtual enviroments.
+% GPU builds\Fix{I don't understance GPU builds. do you mean
+%   GPU vendor/version? give example} and specific CUDA builds. 
+% Changing different virtual environments does not change the CUDA
+% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
+%   GPU) version with Python's virtual environments''?} of the
+% system. 
+% That is why we use Docker when a bug relies on a specific
+% version of CUDA to be installed in the system.
+That is why we use Docker Containers with specific CUDA drivers to reproduce
+such bugs instead of virtual enviroments.
+
+\Fix{Please review and revise}
 

### 2025-01-11 paper/main.tex
u

@@
 \usepackage{xcolor}
+\usepackage{xspace}
+
 %%
@@
 \section{Related Work} 
-Defects4J\cite{just2014defects4j}
-BugsInPy~\cite{widyasari2020bugsinpy}
-Tests4Py~\cite{smytzek2024tests4py}
-Denchmark~\cite{kim2021denchmark}
+Several bug datasets have been proposed in literature for general software. Some
+popular examples includes software-artifact infrastructure repository
+(SIR)~\cite{do2005supporting} which was one of the bug datasets containing 81
+artificial faults in projects across multiple languages,
+Defects4J~\cite{just2014defects4j} which includes 357 real bugs across five
+large real-world Java projects, BugsInPy~\cite{widyasari2020bugsinpy} containing
+493 real bugs from 17 real-world Python programs, and
+BugsJS~\cite{vancsics2020relationship} containing 453 bugs across 10 Javascript
+projects.
+%
+Google's FuzzBench~\cite{metzman2021fuzzbench} provides an evaluation platform
+for comparing general purpose fuzzers. Magma~\cite{hazimeh2020magma} is another
+fuzzing benchmark built by \emph{front-porting} real bugs in latest version of
+projects. In contrast to these general purpose benchmarks, \tname includes
+reproducible bugs for Deep Learning libraries like PyTorch and TensorFlow, and
+allows systematic benchmarking for DLL fuzzers.
+
+% Defects4J\cite{just2014defects4j}
+% BugsInPy~\cite{widyasari2020bugsinpy} Tests4Py~\cite{smytzek2024tests4py}
+% Denchmark~\cite{kim2021denchmark}
 

### 2025-01-11 paper/main.tex
Added method and test oracle

@@
 
-\Fix{Abid, explain the steps you followed to create a bug
-  isntance. For example, (1) selected an issues (according to the
-  criteria defined in 2.1), (2) ...}
+% \Fix{Abid, explain the steps you followed to create a bug
+%   isntance. For example, (1) selected an issues (according to the
+%   criteria defined in 2.1), (2) ...}
+
+In order to add a bug to the dataset, a series of steps are followed.
+
+\begin{itemize}
+  \item A suitable issue is selected following the criteria defined in \ref{sec:selection-criterion}.
+  \item A list of dependencies to reproduced the bug are written on a requirements text (requirements.txt).
+  \item A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
+  \item If the bug depends on a CUDA-specific build, a Dockerfile is written that can create a docker container with the required CUDA-driver installed along with the requirements.txt file and the python script copied into it.
+  \item A script is written that can create the virtual environment or the Docker container and execute the python test.
+  \item All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
+\end{itemize}
+
+\Fix{Please review and revise}
 
@@
 
-\Fix{explain that the test passes if the bug can be reproduced}
+% \Fix{explain that the test passes if the bug can be reproduced}
+
+The bug reproduction code includes python tests (pytest).
+The test oracle is satisfied when the bug is reproduced successfully.
+For bugs that throw an unexpected exception, the test catches the exception and reports the exception details along with a pass status.
+For bugs that result in incorrect output value, assertions are placed in the code to expect the incorrect output value, hence passing the test when the bug occurs.
+For bugs that crash after raising a signal, the code snippet is placed in a seperate file and executed, while the file contaning the actual test asserts the presence of the signal raised by the code.
+Upon successful reproduction, the original code crashes raising the proper signla and the assertion passes.
+
+\Fix{Please review and revise}
 

### 2025-01-11 jax/issue_19035/reproduce_bug.sh
fix: update reproduce_bug.sh for JAX issue #19035 to remove Docker image and clear build cache after use

@@ -45,4 +45,6 @@ fi
 
 docker build -t issue_19035 .
 docker run -it --rm --gpus all issue_19035
+docker rmi -f issue_19035
+docker system prune -f
 exit $?

### 2025-01-11 pytorch/issue_122768/reproduce_bug.sh
fix: update reproduce_bug.sh for PyTorch issue #122768 to remove Docker image and clear build cache after use

@@ -45,4 +45,6 @@ fi
 
 docker build -t issue_122768 .
 docker run -it --rm --gpus all issue_122768
+docker rmi -f issue_122768
+docker system prune -f
 exit $?

### 2025-01-11 paper/main.tex
Added an example of a bug reproduction

@@
 \usepackage{xspace}
-
+\usepackage{listings}
+\lstset{
+  basicstyle=\ttfamily,
+  columns=fullflexible,
+  frame=single,
+  breaklines=true,
+  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
+}
 %%
@@
 
-\Fix{walkthrough an example. Show input and part of output. Explain
-  the output.}
+% \Fix{walkthrough an example. Show input and part of output. Explain
+%   the output.}
+
+Let's take the bug from issue no.
+120903 from \torch.
+To make sure the framework is accessible system wide, the "framework" folder in the tool needs to be added to the PATH environment.
+The command to run a specific test is "run-test".
+To reproduce this bug, the command line prompt is as the following:
+
+\begin{lstlisting}[language=bash]
+  $> run-test --library-name pytorch --bug-id 120903
+\end{lstlisting}
+
+The output will look like this upon reproducing successfully:
+
+\begin{lstlisting}[language=bash]
+  ...
+  Versions of relevant libraries:
+  [pip3] numpy==1.26.4
+  [pip3] torch==2.2.0+cpu
+  [conda] torch                     2.2.0+cpu                pypi_0    pypi
+  ====== test session starts ======
+  platform linux -- Python 3.10.0, pytest-8.2.0, pluggy-1.5.0
+  rootdir: /home/mnaziri/Documents/DL_Testing/dnnbugs/pytorch/issue_120903
+  collected 1 item
+
+  test_issue_120903.py Pytorch issue no. 120903
+  Seed:  120903
+  RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please report a bug to PyTorch. 
+  ====== 1 passed in 0.96s ======
+\end{lstlisting}
+
+In this output, the dependencies used in the reproduction of the bug are listed.
+Then, the pytest is executed and the exception (bug) is caught.
+Afterwards, the issue id is printed and the exception that has been caught is printed to demonstrate the bug.
+At the end, the test is shown to be passed, signifying the successful reproduction of the bug.
+
+\Fix{Please review and revise}
 

### 2025-01-11 pytorch/issue_121725/reproduce_bug.sh
fix: update reproduce_bug.sh for PyTorch issue #121725 to remove Docker image and clear build cache after use

@@ -45,4 +45,6 @@ fi
 
 docker build -t issue_121725 .
 docker run -it --rm --gpus all issue_121725
+docker rmi -f issue_121725
+docker system prune -f
 exit $?

### 2025-01-11 paper/main.tex
Added steps

@@
 
-\Fix{walkthrough an example. Show input and part of output. Explain
-  the output.}
+% \Fix{walkthrough an example. Show input and part of output. Explain
+%   the output.}
+
+To integrate a testing tool such as FreeFuzz, there are two steps:
+
+1. A docker container with the environment of FreeFuzz
+2. A script that takes the name of the library as an argument and run FreeFuzz on the library
+
+To build a docker container for FreeFuzz, the following script can be run:
+
+\begin{lstlisting}[language=bash]
+  $> cd tool-integration/FreeFuzz && bash install_freefuzz_docker.sh
+\end{lstlisting}
+
+Once the docker container is built and is running, providing the name of the container and the location of the script that can execute the tool (either absolute path or relative to the root of the repository) to the command "run-tool" in the framework along with the library and bug id will first reproduce the bug seperately and then update the environment inside the docker to run the tool with the script provided.
+For example, the issue no.
+117033 and the \torch~library, the following command would run FreeFuzz on the enviroment of the bug:
+
+\begin{lstlisting}[language=bash]
+  $> run-tool --container freefuzz --library-name pytorch --bug-id 117033 --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
+\end{lstlisting}
+
+The output looks like the following:
+
+\begin{lstlisting}[language=bash]
+  ...
+  ====== test session starts ======
+  platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
+  ...
+  IndexError: list index out of range
+  ====== 1 passed in 1.09s ======
+  ...
+  Updating environment in the container of the testing tool
+  Successfully copied 16.4kB to freefuzz:/tmp/issue_117033
+  __pycache__  install_environment.sh  reproduce_bug.sh  requirements.txt  test_issue_117033.py
+  ...
+  Running the testing tool on the environment of the bug
+  Testing on  ['torch']
+  torch.log2
+  ...
+  torch.nn.MaxUnpool2d
+  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [1,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
+  ../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [2,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
+  ...
+\end{lstlisting}
+
+Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug.
+Then it proceeds to run the entire testing tool on the enviroment.
+After the execution completes, the output can be checked for all failures produced by FreeFuzz (saved inside the container) and manually inspected to see if any failure that can reveal the bug in question was generated by the tool.
+In this case, the failure generated by FreeFuzz could not generate a failure that can reveal this bug since the API "torch.\_dynamo.export" is not supported by FreeFuzz.
+
+\Fix{Please review and revise}
 

### 2025-01-11 pytorch/issue_121072/test_issue_121072.py
fix: Add assertions to the bug reproduction script for PyTorch issue #121072

@@ -17,12 +17,11 @@ def test_f():
 
     print(get_grads(torch.float32, (128, 128)).flatten())
     print(get_grads(torch.float16, (128, 128)).flatten())
-    print(get_grads(torch.bfloat16, (128, 128)).flatten())
+    assert torch.all(get_grads(torch.float16, (128, 128)).flatten() == 2048) # It appears that the maximum value of the gradient is capped at 2048 for the float16 data type
 
     print(get_grads(torch.float32, (64, 64)).flatten())
     print(get_grads(torch.float16, (64, 64)).flatten())
-    print(get_grads(torch.bfloat16, (64, 64)).flatten())
+    assert torch.all(get_grads(torch.float16, (64, 64)).flatten() == 2048) # It appears that the maximum value of the gradient is capped at 2048 for the float16 data type
 
     print(get_grads(torch.float32, (32, 32)).flatten())
-    print(get_grads(torch.float16, (32, 32)).flatten())
-    print(get_grads(torch.bfloat16, (32, 32)).flatten())
+    print(get_grads(torch.float16, (32, 32)).flatten()) # Correct output for float16

### 2025-01-11 pytorch/issue_120875/reproduce_bug.sh
fix: update reproduce_bug.sh for PyTorch CUDA-based issues to remove Docker image and clear build cache after use
Addresses PyTorch issues: #120875, #120998, #121093, #121253, #121320, #121671, #122085, #122296, #122807

@@ -43,4 +43,6 @@ fi
 
 docker build -t issue_120875 .
 docker run -it --rm --gpus all issue_120875
+docker rmi -f issue_120875
+docker system prune -f
 exit $?

### 2025-01-11 pytorch/issue_120998/reproduce_bug.sh

@@ -44,4 +44,6 @@ fi
 
 docker build -t issue_120998 .
 docker run -it --rm --gpus all issue_120998
+docker rmi -f issue_120998
+docker system prune -f
 exit $?

### 2025-01-11 pytorch/issue_121093/reproduce_bug.sh

@@ -44,4 +44,6 @@ fi
 
 docker build -t issue_121093 .
 docker run -it --rm --gpus all issue_121093
+docker rmi -f issue_121093
+docker system prune -f
 exit $?

### 2025-01-11 pytorch/issue_121320/reproduce_bug.sh

@@ -43,4 +43,6 @@ fi
 
 docker build -t issue_121320 .
 docker run -it --rm --gpus all issue_121320
+docker rmi -f issue_121320
+docker system prune -f
 exit $?

### 2025-01-11 pytorch/issue_122085/reproduce_bug.sh

@@ -43,4 +43,6 @@ fi
 
 docker build -t issue_120085 .
 docker run -it --rm --gpus all issue_120085
+docker rmi -f issue_120085
+docker system prune -f
 exit $?

### 2025-01-11 pytorch/issue_122296/reproduce_bug.sh

@@ -44,4 +44,6 @@ fi
 
 docker build -t issue_122296 .
 docker run -it --rm --gpus all issue_122296
+docker rmi -f issue_122296
+docker system prune -f
 exit $?

### 2025-01-11 paper/main.tex
u
adding screencast link
shortening description of bug instances (table 1)

@@
-\documentclass[sigconf]{acmart}
+\documentclass[sigconf,screen]{acmart}
 
@@
 \acmISBN{978-1-4503-XXXX-X/2018/06}
+\acmBooktitle{Companion Proceedings of the 33rd ACM Symposium on the Foundations
+of Software Engineering (FSE '25), June 23--27, 2025, Trondheim, Norway}
 
@@
   \tf, and \torch.
+\textbf{Screencast}:~\url{https://tinyurl.com/BugsInDLLs}  
 \end{abstract}
@@
 reproduction (Section~\ref{sec:challenges}), and the method we
-followed to create bug instances (Section~\ref{sec:method}). The
-\tname\ database consists of \numbugs{} instances of reproducible bugs
+followed to create bug instances (Section~\ref{sec:method}).
+
+\tname\ contains \numbugs{} instances of reproducible bugs
 representing three popular DL libraries, namely, \jax, \tf, and
@@
 instances for each supported library. Column ``\#'' shows the number
-of bug instances, column ``build'' shows the breakdown of bug
-instances based on releases of the library against those based on
-nightly builds, and column ``environment'' shows the breakdown of bug
-instances that use Python's virtual environment against those that run
-on a Docker container.
+of bug instances, column ``build'' shows the breakdown of instances
+based on the kind of build, and column ``environment'' shows the
+breakdown of instances based on the kind of environment we use to
+reproduce the bug.
 

### 2025-01-11 paper/main.tex
clarifying initial par

@@
 \sloppy Serveral important application domains (e.g., transportation,
-medicine, etc.) use AI to optimize some element of their business
-process. Deep Learning~(DL) libraries, such as \jax, \torch{}, and
-\tf{}, provide the building blocks for the AI components of these
-applications.  Unfortunately, as any piece of software, these
-libraries contain bugs. An impressive number of techniques have been
-recently proposed to find bugs in these libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
-however we observe that the evaluation of
-these techniques do \emph{not} use a reference set of reproducible
-bugs to evaluate their effectiveness. The lack of evaluation standards
-is an obstacle to the fair comparison of techniques, hindering
-research progress.
+medicine, etc.) use AI as part of their business processes. Deep
+Learning~(DL) libraries, such as \jax, \torch{}, and \tf{}, provide
+the building blocks for the AI components of these applications.
+Unfortunately, as any piece of software, these libraries contain
+bugs. An impressive number of techniques have been recently proposed
+to find bugs in these
+libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
+however we observe that the evaluation of these techniques do
+\emph{not} use a reference set of reproducible bugs to evaluate their
+effectiveness. The lack of evaluation standards is an obstacle to the
+fair comparison of techniques, hindering research progress.
 

### 2025-01-11 paper/main.tex
writing in third person

@@
 based on the kind of build, and column ``environment'' shows the
-breakdown of instances based on the kind of environment we use to
-reproduce the bug.
+breakdown of instances based on the kind of environment to reproduce
+the bug.
 

### 2025-01-11 paper/main.tex
pass on selection criteria

@@
   \centering
-  \caption{\label{table:bug-characterization}Characterization of reproducible bugs from \tname.}
+  \caption{\label{table:bug-characterization}Characterization of
+    reproducible bugs from \tname.\Fix{Is this up to date? I have seen
+  lots of activity recently but these numbers remain the same.}}
 \begin{tabular}{l|rrr}
@@
 
-\subsection{Selection Criterion}
+\subsection{Selection Criteria}
 \label{sec:selection-criterion}
@@
 
-Amongst many DL libraries, the most popular libraries for developing AI-enabled applications and used in testing tools are \torch~and \tf.
-\jax~is a relatively newer entry to the list of libraries but it is rapidly gaining popularity as well.
-All three of these libraries are open source with active communities that support the libraries, making them very suitable for developing testing tools around.
-We chose these three popular datasets in order to enhance the process of developing testing tools around these libraries.
+\textbf{Libraries.}~\torch~and \tf are popular DL libraries
+intensively used in the literature. \jax\ is a newer library that has
+been rapidly gaining popularity. All these libraries are open source
+with active communities supporting their maintenaance.
+
+%% We chose these three popular datasets in order to enhance the process
+%% of developing testing tools around these libraries.
 
@@
 
-For the bugs from these libraries, we focused on bug reports that have been accepted by the developer community as true bugs.
-We determine this by checking whether the bugs have appropriate labels and have been fixed with pull requests linked to them.
-Among these confirmed bug reports, we choose the ones that have enough information to reproduce the bugs i.e.
-code to reproduce the bug, enviroment required for reproduction, clear description of desired behavior etc.
-Once we can successfully reproduce the bug by creating the enviroment detailed in the report, we choose the bug to be included in our dataset.
-
-\Fix{Please review and revise}
+\textbf{Bugs.}~We focused on bug reports that have been accepted by
+the developer community as true bugs. We determine this by checking
+whether the bugs have appropriate labels and have been fixed with pull
+requests linked to them. Among these confirmed bug reports, we choose
+the ones that have enough information to reproduce the bugs, i.e.,
+code to reproduce the bug, enviroment required for
+reproduction\Fix{Abid, can you confirm that environment here is not
+  the same as venv-docker that we are using on Table 1? instead it
+  means the version of CUDA, libraries, etc.? If so, avoid using the
+  word environment.}, clear description of the desired behavior,
+etc. Once we can successfully reproduce the bug by creating the
+enviroment detailed in the report, we choose the bug to be included in
+our dataset.
 

### 2025-01-12 paper/main.tex
challenges

@@
 
-\textbf{Handling bugs from nighly builds requires saving wheels.}  Many
-of the reproducible bugs rely on nightly builds of the
-libraries. These builds are available for a limited amount of time. In
-order to ensure bugs reported on these builds to remain reproducible,
-it is imperative to save wheel files~\cite{wheels} for the
-correspondind builds.
+\textbf{Handling bugs from nighly builds requires saving wheels.}
+Many of the reproducible bugs rely on the libraries' nightly builds,
+which are available for a limited amount of time. To ensure that bugs
+reported on these builds remain reproducible, it is necessary to save
+Python wheel files (.whl)~\cite{wheels} for the correspondind builds.
 
 \textbf{Handling bugs in specific GPU-CUDA versions requires OS
-  changes:} Many of the GPU-related bugs can only be reproduced with
-library versions that are built with specific versions of CUDA.
-These builds require those specific CUDA drivers to be installed on
-the system, and the version of the CUDA driver installed on a system
-can not be changed with Python's virtual enviroments.
+  changes:} Some GPU-related bug instances can only be reproduced with
+specific versions of CUDA~\cite{cuda}, NVIDIA's platform and API for
+programming GPUs. These instances require specific CUDA drivers to be
+installed on the system. Python virtual enviroments are not designed
+to enable change of OS drivers.
 % GPU builds\Fix{I don't understance GPU builds. do you mean
@@
 % version of CUDA to be installed in the system.
-That is why we use Docker Containers with specific CUDA drivers to reproduce
-such bugs instead of virtual enviroments.
+We use Docker containers for the bug instances that require changes in
+drivers.
 

### 2025-01-12 paper/main.tex
challenges
pass on section 2.3

@@
 \usepackage{listings}
+\usepackage{enumitem}
 \lstset{
@@
     reproducible bugs from \tname.\Fix{Is this up to date? I have seen
-  lots of activity recently but these numbers remain the same.}}
+  lots of activity recently but these numbers remain the
+  same.}\Fix{Can we add info about whether Python and/or C code causes
+      the bug?}\Fix{Can we add info on whether it is GPU related
+      (i.e., only manifests in GPUs)?}}
 \begin{tabular}{l|rrr}
@@
 % version of CUDA to be installed in the system.
-We use Docker containers for the bug instances that require changes in
-drivers.
-
-\Fix{Please review and revise}
+We use Docker containers~\cite{merkel2014docker} for the bug instances
+that require changes in drivers.
 
@@
 
-% \Fix{Abid, explain the steps you followed to create a bug
-%   isntance. For example, (1) selected an issues (according to the
-%   criteria defined in 2.1), (2) ...}
+The following steps show the method we use to create bug instances:
 
-In order to add a bug to the dataset, a series of steps are followed.
-
-\begin{itemize}
-  \item A suitable issue is selected following the criteria defined in \ref{sec:selection-criterion}.
-  \item A list of dependencies to reproduced the bug are written on a requirements text (requirements.txt).
-  \item A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
-  \item If the bug depends on a CUDA-specific build, a Dockerfile is written that can create a docker container with the required CUDA-driver installed along with the requirements.txt file and the python script copied into it.
-  \item A script is written that can create the virtual environment or the Docker container and execute the python test.
-  \item All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
-\end{itemize}
-
-\Fix{Please review and revise}
+\begin{enumerate}[leftmargin=0.5cm]
+  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
+  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug;
+  \item Create a file showing the code that causes the bug (for documentation);
+  \item Create a file with a \CodeIn{pytest} test case that passes if
+    the code triggers the buggy behavior documented in the issue;
+    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
+  \item If the bug depends on a CUDA-specific build, write a
+    Dockerfile to create a container including the needed CUDA-driver
+    and the other artifacts mentioned above (e.g., test file and
+    requirements);
+    %% along with the requirements.txt file and the python
+    %% script copied into it.
+  \item Write a script that creates the virtual environment (either
+    Python's \CodeIn{venv}~\cite{venv} or Docker container) and runs
+    the test on it;
+  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
+    artifacts mentioned above, where \CodeIn{lib} refers to the
+    affected library and \CodeIn{bug-id} is a fresh identifier of the
+    bug instance.
+    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
+\end{enumerate}
 

### 2025-01-12 paper/main.tex
pass on tool integration

@@
 
-\section{\tname: Database of Bugs in DL libraries}
-\subsection{Bug Interface}
+\textbf{Test Oracles.}~
+The bug reproduction code includes python tests (pytest). The test
+oracle is satisfied when the bug is reproduced successfully. For bugs
+that throw an unexpected exception, the test catches the exception and
+reports the exception details along with a pass status. For bugs that
+result in incorrect output value, assertions are placed in the code to
+expect the incorrect output value, hence passing the test when the bug
+occurs. For bugs that crash after raising a signal, the code snippet
+is placed in a seperate file and executed, while the file contaning
+the actual test asserts the presence of the signal raised by the
+code. Upon successful reproduction, the original code crashes raising
+the proper signla and the assertion passes.\Fix{Please review and
+  revise}
+
+\textbf{Example}~\Fix{Can you show here the artifacts associated to bug
+  120903 that you will use in the next section? If it takes too much
+  space, show only directory with files and the test case.}
+
+\section{\tname} % : Database of Bugs in DL libraries
+
+This section presents the interface of \tname\ and walks the reader
+through a demonstration showing the tool's functionality.
+
+\subsection{Interface}
 
@@
   \toprule
+  \textbf{command} & \textbf{description} \\
+  \midrule
 list-tests & List the tests available on this dataset\\
@@
 run-tests & Runs all the tests\\
+run-tool & Runs a testing tool in a given buggy environment \\
 show-info & Shows information about the tests available on this benchmark\\
@@
 
-Table~\ref{table:bug-interface} shows \Fix{...}
-
-\subsection{Test Oracle}
-
+Table~\ref{table:bug-interface} shows the list of commands in the
+\tname's interface along with a short description for these
+commands. In the following we demonstrate \tname.
 % \Fix{explain that the test passes if the bug can be reproduced}
 
-The bug reproduction code includes python tests (pytest).
-The test oracle is satisfied when the bug is reproduced successfully.
-For bugs that throw an unexpected exception, the test catches the exception and reports the exception details along with a pass status.
-For bugs that result in incorrect output value, assertions are placed in the code to expect the incorrect output value, hence passing the test when the bug occurs.
-For bugs that crash after raising a signal, the code snippet is placed in a seperate file and executed, while the file contaning the actual test asserts the presence of the signal raised by the code.
-Upon successful reproduction, the original code crashes raising the proper signla and the assertion passes.
+\subsection{Usage}
 
-\Fix{Please review and revise}
+To enable system-wide access of the framework, it is necessary to add
+the directory \CodeIn{/framework} to the \CodeIn{PATH} environment
+variable. Run the following commands for that:
 
-\subsection{Usage and Setup}
+\begin{lstlisting}[language=bash]
+$> git clone git@github.com:ncsu-swat/bugsindlls.git
+$> cd bugsindlls
+$> export PATH=$PATH:`pwd`/framework
+\end{lstlisting}
 
@@
 
-Let's take the bug from issue no.
-120903 from \torch.
-To make sure the framework is accessible system wide, the "framework" folder in the tool needs to be added to the PATH environment.
-The command to run a specific test is "run-test".
-To reproduce this bug, the command line prompt is as the following:
+Let us use the bug 120903~\Fix{cite} from \torch\ to demonstrate the
+command \CodeIn{run-test}, which runs a test to reproduce a bug on an
+environment with the necessary dependencies installed. Use the
+following command to reproduce the bug:
 
@@
 
-The output will look like this upon reproducing successfully:
+\noindent
+Execution of this command produces the following output:
 
@@
 
-In this output, the dependencies used in the reproduction of the bug are listed.
-Then, the pytest is executed and the exception (bug) is caught.
-Afterwards, the issue id is printed and the exception that has been caught is printed to demonstrate the bug.
-At the end, the test is shown to be passed, signifying the successful reproduction of the bug.
+The output shows the dependencies installed in the environment to
+reproduce the bug and the verdict of the test oracle from pytest. In
+this case, the execution of the bug-revealing test throws a runtime
+error. Note that this test passes as it reproduces the intended bug.
 
-\Fix{Please review and revise}
+%% Afterwards, the issue
+%% id is printed and the exception that has been caught is printed to
+%% demonstrate the bug. At the end, the test is shown to be passed,
+%% signifying the successful reproduction of the bug.
+
+%% \Fix{Please review and revise}
 
@@
 
+Tool execution proceeds in two steps: (1) Creation of Docker container
+associated with a tool and (2) Execution of the tool.  The following
+script executes the first step, i.e., it builds a Docker container for
+FreeFuzz:
+
 % \Fix{walkthrough an example. Show input and part of output. Explain
 %   the output.}
-
-To integrate a testing tool such as FreeFuzz, there are two steps:
-
-1. A docker container with the environment of FreeFuzz
-2. A script that takes the name of the library as an argument and run FreeFuzz on the library
-
-To build a docker container for FreeFuzz, the following script can be run:
+%% The user needs to execute two steps to integrate a testing tool (e.g.,
+%% FreeFuzz) on \tname.
+%% 1. Create a docker container for the tool
+%% 2. A script that takes the name of the library as an argument and run FreeFuzz on the library
 
@@
 \end{lstlisting}
+
+\Fix{I am here -Marcelo}
 

### 2025-01-13 paper/main.tex
minor changes

@@
   \tf, and \torch.
-\textbf{Screencast}:~\url{https://tinyurl.com/BugsInDLLs}  
+\textbf{Screencast}:~\url{https://tinyurl.com/BugsInDLLs}\\
+\textbf{GitHub repository}:~\url{https://github.com/ncsu-swat/bugsindlls}    
 \end{abstract}
@@
 
-This paper presents \tname, a database of curated reproducible bugs to
+We present \tname, a database of curated reproducible bugs to
 enable credible evaluation of DL library testing techniques. \tname\ is
@@
 of bug instances, column ``build'' shows the breakdown of instances
-based on the kind of build, and column ``environment'' shows the
-breakdown of instances based on the kind of environment to reproduce
-the bug.
+for each kind of build, and column ``environment'' shows the breakdown
+of instances for each kind of environment to reproduce the bug.
 
@@
 been rapidly gaining popularity. All these libraries are open source
-with active communities supporting their maintenaance.
+with active communities supporting their maintenance.
 
@@
   the same as venv-docker that we are using on Table 1? instead it
-  means the version of CUDA, libraries, etc.? If so, avoid using the
+  means the version of CUDA, libraries, etc.? If so, avoid (re)using the
   word environment.}, clear description of the desired behavior,

### 2025-01-13 paper/main.tex
another pass

@@
   \tf, and \torch.
-\textbf{Screencast}:~\url{https://tinyurl.com/BugsInDLLs}\\
-\textbf{GitHub repository}:~\url{https://github.com/ncsu-swat/bugsindlls}    
 \end{abstract}
@@
 equipped with a command-line interface to enable researchers to analyze
-and reproduce bug instances.
+and reproduce bug instances. The following screencast demonstrate some
+of the features in \tname:
+
+\url{https://tinyurl.com/BugsInDLLs}\\
+
+\tname\ has been under active development since March 21, 2024, the
+day of the first commit in the corresponding GitHub repository. Two
+UROP students, two PhD students, and two faculty were involved in the
+work. \tname\ is publicly available from the following URL:
+
+\url{https://github.com/ncsu-swat/bugsindlls}
 
@@
 Tool execution proceeds in two steps: (1) Creation of Docker container
-associated with a tool and (2) Execution of the tool.  The following
-script executes the first step, i.e., it builds a Docker container for
-FreeFuzz:
+associated with a tool and (2) Execution of the tool.  Let us
+demonstrate this process on FreeFuzz~\cite{wei2022free}, an API-level
+fuzzer for DL libraries. The following script executes the first step
+of the two-step integration method.
+
+%i.e., it builds a Docker container for FreeFuzz:
 
@@
 
-\Fix{I am here -Marcelo}
+\noindent
+The script \CodeIn{install\_freefuzz\_docker.sh} contains the
+following instructions:
 
-Once the docker container is built and is running, providing the name of the container and the location of the script that can execute the tool (either absolute path or relative to the root of the repository) to the command "run-tool" in the framework along with the library and bug id will first reproduce the bug seperately and then update the environment inside the docker to run the tool with the script provided.
-For example, the issue no.
-117033 and the \torch~library, the following command would run FreeFuzz on the enviroment of the bug:
+\begin{lstlisting}[language=bash]
+#!/bin/bash
+git clone https://github.com/ise-uiuc/FreeFuzz.git
+docker build -t freefuzz .
+docker run --name freefuzz --gpus all -d freefuzz:latest
+docker exec -it freefuzz mongorestore dump/
+\end{lstlisting}
+
+%\Fix{I am here -Marcelo}
+%% Once the docker container is built and is running, providing the name
+%% of the container and the location of the script that can execute the
+%% tool (either absolute path or relative to the root of the repository)
+%% to the command
+
+The second step runs the \tname's command \CodeIn{run-tool}, which
+proceeds in two steps (1) reproduce the bug separately, as done with
+command \CodeIn{run-test}, and (2) then update the environment inside
+the docker container of the tool to run the tool with the script
+provided.\Fix{is the container destroyed after that? you are changing
+  the environment for a certain bug, right?!} The first step is a
+sanity check to assure that the bug can indeed be reproduced. For
+example, the following command runs FreeFuzz on the enviroment of the
+bug associated with the issue 117033 from \torch.
 
@@
 
+\Fix{Consider the comments from Saikat, please.}
 Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug.
@@
 \section{\tname: Use cases}
+
+\Fix{@Saikat, can you please write 1-2 sentences about each use case here?}
 
@@
 
+\Fix{Marcelo will write a paragraph}
+
 \bibliographystyle{ACM-Reference-Format}
@@
 
-\section{Research Methods}
+\section{Walkthrough}
+
+\Fix{}
 

### 2025-01-14 paper/main.tex
fixed some comments

@@
   lots of activity recently but these numbers remain the
-  same.}\Fix{Can we add info about whether Python and/or C code causes
-      the bug?}\Fix{Can we add info on whether it is GPU related
-      (i.e., only manifests in GPUs)?}}
+  same - Fixed (Abid)}\Fix{Can we add info about whether Python and/or C code causes
+      the bug? - Abid: we report how many c,python and cuda native files are buggy in total but not per bug, so currently no}\Fix{Can we add info on whether it is GPU related
+      (i.e., only manifests in GPUs)? - Abid: venv-docker is the same as cpu-gpu}}
 \begin{tabular}{l|rrr}
@@
   \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
-  \\ \cmidrule(lr){2-4} \jax{} & 44 & 43-1 & 43-1 \\ \torch{} & 33 &
-  15-18 & 19-14 \\ \tf{} & 25 & 24-1 & 25-0 \\ \midrule
-  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15
+  \\ \cmidrule(lr){2-4} \jax{} & 46 & 45-1 & 45-1 \\ \torch{} & 37 &
+  18-19 & 21-16 \\ \tf{} & 24 & 23-1 & 24-0 \\ \midrule
+  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 86-21& 90-17
   \\ \bottomrule

### 2025-01-14 paper/main.tex
fixed the usage of the word environment

@@
 the ones that have enough information to reproduce the bugs, i.e.,
-code to reproduce the bug, enviroment required for
-reproduction\Fix{Abid, can you confirm that environment here is not
-  the same as venv-docker that we are using on Table 1? instead it
-  means the version of CUDA, libraries, etc.? If so, avoid (re)using the
-  word environment.}, clear description of the desired behavior,
+code to reproduce the bug, dependencies required for the bug
+reproduction
+% \Fix{Abid, can you confirm that environment here is not
+%   the same as venv-docker that we are using on Table 1? instead it
+%   means the version of CUDA, libraries, etc.? If so, avoid (re)using the
+%   word environment.}
+, clear description of the desired behavior,
 etc. Once we can successfully reproduce the bug by creating the

### 2025-01-14 paper/main.tex
added some comments

@@
   120903 that you will use in the next section? If it takes too much
-  space, show only directory with files and the test case.}
+  space, show only directory with files and the test case. - Abid: by the test case, do you mean the python code used to reproduce the bug?}
 
@@
 provided.\Fix{is the container destroyed after that? you are changing
-  the environment for a certain bug, right?!} The first step is a
+  the environment for a certain bug, right?!
+- Abid: the dependencies are installed inside the docker, but after running the dependencies are not reverted back.
+if another bug is to be reproduced, installing the new dependencies will simply overwrite the previous dependencies} The first step is a
 sanity check to assure that the bug can indeed be reproduced. For

### 2025-01-14 paper/main.tex
Modified FreeFuzz code according to comments

@@
   ...
+  [Reproducing the bug]
   ====== test session starts ======
@@
   ...
+  [Setting up FreeFuzz]
   Updating environment in the container of the testing tool
@@
   ...
+  [Running FreeFuzz]
   Running the testing tool on the environment of the bug
@@
 
-\Fix{Consider the comments from Saikat, please.}
+% \Fix{Consider the comments from Saikat, please.}
 Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug.

### 2025-01-14 paper/main.tex
Updated environment details to conda

@@
   \item Write a script that creates the virtual environment (either
-    Python's \CodeIn{venv}~\cite{venv} or Docker container) and runs
+    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
     the test on it;

### 2025-01-14 paper/main.tex
Added test code example

@@
 code. Upon successful reproduction, the original code crashes raising
-the proper signla and the assertion passes.\Fix{Please review and
+the proper signal and the assertion passes.\Fix{Please review and
   revise}
 
-\textbf{Example}~\Fix{Can you show here the artifacts associated to bug
-  120903 that you will use in the next section? If it takes too much
-  space, show only directory with files and the test case. - Abid: by the test case, do you mean the python code used to reproduce the bug?}
+\textbf{Example}
+% ~\Fix{Can you show here the artifacts associated to bug
+%   120903 that you will use in the next section? If it takes too much
+%   space, show only directory with files and the test case. - Abid: by the test case, do you mean the python code used to reproduce the bug?} 
+  The issue no. 120903 in pytorch has the following test code that checks the oracle:
+
+\begin{lstlisting}[language=python]
+def test_f():
+  input_data = torch.randn(3, 4, 5, 6)
+  scale = np.array([0.1, 0.2, 0.3, 0.4])
+  zero_point = torch.tensor([1, 2, 3, 4], dtype=torch.int32)
+  axis = 1
+  quant_min = 0
+  quant_max = 255
+  with pytest.raises(RuntimeError) as e_info:
+      output = torch.fake_quantize_per_channel_affine(input_data, torch.from_numpy(scale), zero_point, axis, quant_min, quant_max)
+  print(f'{e_info.type.__name__}: {e_info.value}')
+\end{lstlisting}
 

### 2025-01-14 paper/main.tex
conclusion half way

@@
 equipped with a command-line interface to enable researchers to analyze
-and reproduce bug instances. The following screencast demonstrate some
-of the features in \tname:
+and reproduce bug instances. The following screencast demonstrates some
+of the features of \tname:
 
@@
 \tname\ has been under active development since March 21, 2024, the
-day of the first commit in the corresponding GitHub repository. Two
-UROP students, two PhD students, and two faculty were involved in the
-work. \tname\ is publicly available from the following URL:
+day of the first commit in its GitHub repository. Two UROP students,
+two PhD students, and two faculty were involved in the work during
+this period. \tname\ is publicly available from the following URL:
 
@@
   \caption{\label{table:bug-characterization}Characterization of
-    reproducible bugs from \tname.\Fix{Is this up to date? I have seen
-  lots of activity recently but these numbers remain the
-  same - Fixed (Abid)}\Fix{Can we add info about whether Python and/or C code causes
-      the bug? - Abid: we report how many c,python and cuda native files are buggy in total but not per bug, so currently no}\Fix{Can we add info on whether it is GPU related
-      (i.e., only manifests in GPUs)? - Abid: venv-docker is the same as cpu-gpu}}
+    reproducible bugs from \tname.}
+  %%   \Fix{Is this up to date? I have seen
+  %% lots of activity recently but these numbers remain the
+  %% same - Fixed (Abid)}\Fix{Can we add info about whether Python and/or C code causes
+  %%     the bug? - Abid: we report how many c,python and cuda native files are buggy in total but not per bug, so currently no}\Fix{Can we add info on whether it is GPU related
+  %%     (i.e., only manifests in GPUs)? - Abid: venv-docker is the same
+  %%     as cpu-gpu}}
 \begin{tabular}{l|rrr}
@@
 
+In this example, the unexpected behavior is a \CodeIn{RuntimeError} thrown by the call to the \CodeIn{fake\_quantize\_per\_channel\_affine} API from \torch.
+Since the test oracle should pass when the bug is successfully reproduced, the code catches the exception and prints information about it, and upon catching the exception successfully, the test passes.
+If the bug reproduction fails i.e.
+the exception is not thrown or a different exception is thrown, the test will fail.
+
 \section{\tname} % : Database of Bugs in DL libraries
@@
 \subsection{Usage}
+\label{sec:usage}
 
@@
 the docker container of the tool to run the tool with the script
-provided.\Fix{is the container destroyed after that? you are changing
-  the environment for a certain bug, right?!
-- Abid: the dependencies are installed inside the docker, but after running the dependencies are not reverted back.
-if another bug is to be reproduced, installing the new dependencies will simply overwrite the previous dependencies} The first step is a
-sanity check to assure that the bug can indeed be reproduced. For
-example, the following command runs FreeFuzz on the enviroment of the
-bug associated with the issue 117033 from \torch.
+provided. The first step is a sanity check to assure that the bug can
+indeed be reproduced. For example, the following command runs FreeFuzz
+on the enviroment of the bug associated with the issue 117033 from
+\torch.
 
@@
 ...
+
 [Setting up FreeFuzz]
@@
 ...
+
 [Running FreeFuzz]
@@
 
-\Fix{Please review and revise}
-
 \section{\tname: Use cases}
 
-\Fix{@Saikat, can you please write 1-2 sentences about each use case here?}
-
-\subsection{Evaluating DL library testing techniques}
-\subsection{Fault Detection}
-\subsection{Program Repair}
+We anticipate two major use cases for \tname: (1) \textbf{evaluation
+  of testing techniques} and (2) \textbf{evaluation of repair
+  techniques}. Dozens of API- and model-level testing techniques have
+been proposed in the literature recently and it is imperative to
+evaluate them using a standard benchmark. \tname\ provides such
+benchmark. Considering repair, as testing techniques mature it becomes
+important to identify candidate repairs that can be recommended to
+developers when reporting issues in bug trackers. With \tname\ it is
+possible to identify if the problem has been resolved.
 
 \section{Related Work}
-Several bug datasets have been proposed in literature for general software. Some
-popular examples includes software-artifact infrastructure repository
-(SIR)~\cite{do2005supporting} which was one of the bug datasets containing 81
-artificial faults in projects across multiple languages,
-Defects4J~\cite{just2014defects4j} which includes 357 real bugs across five
-large real-world Java projects, BugsInPy~\cite{widyasari2020bugsinpy} containing
-493 real bugs from 17 real-world Python programs, and
-BugsJS~\cite{vancsics2020relationship} containing 453 bugs across 10 Javascript
-projects.
+
+Several bug datasets have been proposed in literature for general
+software. Some popular examples includes software-artifact
+infrastructure repository (SIR)~\cite{do2005supporting} which was one
+of the bug datasets containing 81 artificial faults in projects across
+multiple languages, Defects4J~\cite{just2014defects4j} which includes
+357 real bugs across five large real-world Java projects,
+BugsInPy~\cite{widyasari2020bugsinpy} containing 493 real bugs from 17
+real-world Python programs, and BugsJS~\cite{vancsics2020relationship}
+containing 453 bugs across 10 Javascript projects.
 %
@@
 \section{Conclusion and Future Work}
+Deep Learning (DL) Libraries (e.g., \torch) provide the basic blocks
+for creating AI-enabled applications, which are becoming very
+popular. Several testing techniques have been proposed in the
+literature to find bugs on these libraries. Unfortunately, the lack of
+a dataset of reproducible bugs in those libraries poses a barrier to
+a proper evaluation of these techniques. \tname{} fills the gaps by
 
-\Fix{Marcelo will write a paragraph}
-
+\balance
 \bibliographystyle{ACM-Reference-Format}
@@
 
-\Fix{}
+Section~\ref{sec:usage} demonstrates usage of \tname. The reader can
+also follow the steps in the README.md file on our GitHub repository.
 

### 2025-01-14 paper/main.tex
another pass

--- 2025-01-14 paper/main.tex
@@
 popular. Several testing techniques have been proposed in the
-literature to find bugs on these libraries. Unfortunately, the lack of
-a dataset of reproducible bugs in those libraries poses a barrier to
-a proper evaluation of these techniques. \tname{} fills the gaps by
+literature to find bugs in these libraries. Unfortunately, the lack of
+a dataset of reproducible bugs in those libraries poses an important
+barrier to the proper evaluation of these techniques. \tname{} fills
+the gaps. It includes a total of \numbugs\ across three major DL
+libraries. We plan to continue expanding this dataset and to explore
+automated approaches to extract patches from issue trackers and
+``frontport'' them~\cite{hazimeh2020magma} to a single version of the
+library to facilitate testing.
 

### 2025-01-14 paper/main.tex
fixed remaining comments

@@
 code. Upon successful reproduction, the original code crashes raising
-the proper signal and the assertion passes.\Fix{Please review and
-  revise}
+the proper signal and the assertion passes.
+% \Fix{Please review and revise}
 
@@
 
-Let us use the bug 120903~\Fix{cite} from \torch\ to demonstrate the
+Let us use the bug 120903~\cite{torch120903} from \torch\ to demonstrate the
 command \CodeIn{run-test}, which runs a test to reproduce a bug on an

### 2025-01-14 paper/main.tex
highlight

@@
   postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
+  escapeinside={(*@}{@*)},
 }
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash,keywords={}]
 $> cd tool-integration/FreeFuzz && bash install_freefuzz_docker.sh
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash,keywords={}]
 #!/bin/bash
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash,keywords={}]
 $> run-tool --container freefuzz --library-name pytorch --bug-id 117033 --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash,keywords={}]
 ...  
-[Reproducing the bug]
+(*@\textbf{[Reproducing the bug]}@*)
 ====== test session starts ======
@@
 
-[Setting up FreeFuzz]
+(*@\textbf{[Setting up FreeFuzz]}@*)
 Updating environment in the container of the testing tool
@@
 
-[Running FreeFuzz]
+(*@\textbf{[Running FreeFuzz]}@*)
 Running the testing tool on the environment of the bug

### 2025-01-15 paper/main.tex
Updated citation and author
Fixed a type

@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato et al.}
+\renewcommand{\shortauthors}{Naziri et al.}
 
@@
 
-\textbf{Handling bugs from nighly builds requires saving wheels.}
+\textbf{Handling bugs from nightly builds requires saving wheels.}
 Many of the reproducible bugs rely on the libraries' nightly builds,

### 2025-01-16 tool-integration/FreeFuzz/install_freefuzz_docker.sh
Fixed errors with already existing clone repo and python command not working in freefuzz docker

@@ -1,6 +1,13 @@
 #!/bin/bash
 
-git clone https://github.com/ise-uiuc/FreeFuzz.git
+if [ ! -d FreeFuzz ] ; then
+    git clone https://github.com/ise-uiuc/FreeFuzz.git FreeFuzz
+else
+    cd FreeFuzz
+    git pull https://github.com/ise-uiuc/FreeFuzz.git
+    cd ..
+fi
+
 docker build -t freefuzz .
 docker run --name freefuzz --gpus all -d freefuzz:latest
 docker exec -it freefuzz mongorestore dump/

### 2025-03-18 paper/main.tex
Added comments in the paper

@@
 fair comparison of techniques, hindering research progress.
+\Fix{Clarify how the "evaluation set" used by the existing works is different from the "reference set" that we are proposing. Also, need more compelling reason/some sort of evaluation of other fuzzers
+to complement the motivation}
 
@@
 
+\Fix{Need to add what labels were used, which period we took the issues from,
+how many issues we looked at, define "bug reports", mention how many bugs had 
+been filtered with each criterion}
+
 \textbf{Bugs.}~We focused on bug reports that have been accepted by
@@
   \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
-  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug;
+  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug; \Fix{Clarify that the version of the library which was used to report the bug is also included in the requirements.txt file}
   \item Create a file showing the code that causes the bug (for documentation);
@@
 
+\Fix{What evaluation can be added to this section?}
 \subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}
@@
 possible to identify if the problem has been resolved. 
+\Fix{The concept of repairing has not been tied to any commands in the tool. Suggestions include
+a way to recreate an enviroment with the bug fixed, or a way to check if the bug has been fixed in a new version of the library.}
 

### 2025-03-18 paper/main.tex
Added comment about bugsinpy
Reduced fontsize of code snippets

@@
 
+\Fix{Need to add text regarding differentiating the tool from BugsInPy}
+
 \section{Objects and Methods}
@@
 
-\begin{lstlisting}[language=python]
+\begin{lstlisting}[language=python,basicstyle=\small,]
 def test_f():
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash,basicstyle=\small,]
 $> git clone git@github.com:ncsu-swat/bugsindlls.git
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash,basicstyle=\small,]
 $> run-test --library-name pytorch --bug-id 120903
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash,basicstyle=\small,]
 ... 
@@
 
-\begin{lstlisting}[language=bash,keywords={}]
+\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
 $> cd tool-integration/FreeFuzz && bash install_freefuzz_docker.sh
@@
 
-\begin{lstlisting}[language=bash,keywords={}]
+\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
 #!/bin/bash
@@
 
-\begin{lstlisting}[language=bash,keywords={}]
+\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
 $> run-tool --container freefuzz --library-name pytorch --bug-id 117033 --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
@@
 
-\begin{lstlisting}[language=bash,keywords={}]
+\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
 ...  

### 2025-03-19 framework/stats.py
Add Bug library version breakdown in stats

@@ -59,6 +59,9 @@ def process_file(libname, print_fmt, total_bugs):
         num_cuda = 0  
         ##
         num_nightly = 0
+        ##
+        bug_library_version = {}
+
         for row in csv_reader:
             if row["Reproduced"] == "Yes":
                 total_bugs += 1
@@ -99,6 +102,15 @@ def process_file(libname, print_fmt, total_bugs):
                 if row["Nightly"].lower().strip() == "yes":
                     num_nightly += 1
 
+                # bug library versions
+                bug_l_version = row["Buggy Version"].strip()
+                if bug_l_version == "":
+                    print(f"\nWARNING: {row['Issue #']} does not have a library version")
+                if bug_l_version not in bug_library_version:
+                    bug_library_version[bug_l_version] = [row['Issue #']]
+                else:
+                    bug_library_version[bug_l_version].append(row['Issue #'])
+
         print(f'  # Total: {total_bugs - initial_bugs}')
         print(f'  # Require GPU: {num_gpus} ({num_gpus*100/(num_gpus+num_cpus):.2f}%)')
         print(f'  # Do NOT Require GPU: {num_cpus} ({num_cpus*100/(num_gpus+num_cpus):.2f}%)')        
@@ -115,7 +127,14 @@ def process_file(libname, print_fmt, total_bugs):
                 print(f'    {bug_m_type}: {bug_manifest_type[bug_m_type]}')
             else:
                 print(f'    <undefined>: {bug_manifest_type[bug_m_type]}')
-    
+        print('----------------------------')
+        print(f'  # Bug library version breakdown:')
+        for bug_l_version in bug_library_version.keys():
+            if bug_l_version.strip() > "":
+                print(f'    {bug_l_version}: {", ".join(bug_library_version[bug_l_version])} (Total: {len(bug_library_version[bug_l_version])})')
+            else:
+                print(f'    <undefined>: {", ".join(bug_library_version[bug_l_version])} (Total: {len(bug_library_version[bug_l_version])})')
+
     if (print_fmt == "trie") or (print_fmt == "both"):
         print('----------------------------')
         print(tr)             

### 2025-03-19 paper/main.tex
Added selection criteria

@@
 been rapidly gaining popularity. All these libraries are open source
-with active communities supporting their maintenance.
+with active communities supporting their maintenance. From these three
+libraries, we selected issue reports from specific periods in their
+respective issue trackers. For \torch, we selected issues from the
+period between \torchfrom and \torchto. For \tf, we selected issues
+from the period between \tffrom and \tfto. For \jax, we selected
+issues from the period between \jaxfrom and \jaxto. We have chosen
+different periods for each library depending on the number of issues
+reported in the issue tracker in that period. For example, \tf has a
+much longer period compared to the others because the frequency of
+issues reported in the issue tracker is lower.
 
@@
 
-\Fix{Need to add what labels were used, which period we took the issues from,
-how many issues we looked at, define "bug reports", mention how many bugs had 
-been filtered with each criterion}
+% \Fix{Need to add what labels were used, which period we took the issues from,
+% how many issues we looked at, define "bug reports", mention how many bugs had 
+% been filtered with each criterion}
 
-\textbf{Bugs.}~We focused on bug reports that have been accepted by
+\textbf{Bugs.}~We focus on issue reports that have been accepted by
 the developer community as true bugs. We determine this by checking
-whether the bugs have appropriate labels and have been fixed with pull
-requests linked to them. Among these confirmed bug reports, we choose
-the ones that have enough information to reproduce the bugs, i.e.,
+whether the issue reports have the label "bug" and have been fixed with pull
+requests linked to them. We then create a filter that incorporates
+the periods mentioned above, the label, the issue status being closed
+and the presence of a linked pull request. We found \numtorchfiltered{}
+issues for \torch, \numtffiltered{} issues for \tf, and \numjaxfiltered{}
+issues for \jax after filtering the issues. \torch has the highest number
+of issues due to a lack of a label for bugs in the issue tracker.
+
+We then manually inspect the
+filtered issues to ensure that they contain enough information to
+reproduce the bug, i.e.,
 code to reproduce the bug, dependencies required for the bug
-reproduction
+reproduction, clear description of the desired behavior,
+etc. We also filter bugs that are not in the core functionality
+of the library e.g. documentation issues, feature requests, etc.
+After this stage of manual inspection, we end up with \numtorchinspected{}
+issues for \torch, \numtfinspected{} issues for \tf, and \numjaxinspected{}
+issues for \jax.
+
+% Among these confirmed bug reports, we choose
+% the ones that have enough information to reproduce the bugs, i.e.,
+% code to reproduce the bug, dependencies required for the bug
+% reproduction
 % \Fix{Abid, can you confirm that environment here is not
@@
 %   word environment.}
-, clear description of the desired behavior,
-etc. Once we can successfully reproduce the bug by creating the
+% , clear description of the desired behavior,
+% etc. 
+Afterwards, we assess the reproducibility of the bug by creating a
+virtual environment that contains the necessary dependencies to
+reproduce the bug.
+Once we can successfully reproduce the bug by creating the
 enviroment detailed in the report, we choose the bug to be included in
-our dataset.
+our dataset. Through this process, we end up with \numtorchselected{},
+\numtfselected{}, and \numjaxselected{} bug instances for \torch, \tf,
+and \jax, respectively.
+
+\Fix{Abid: Added what labels were used, which period we took the issues from,
+how many issues we looked at, defined "bug reports", mentioned how many bugs had 
+been filtered with each criterion. Please review and revise}
 

### 2025-03-20 paper/main.tex
Added contribution steps

@@
   \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
-  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug; \Fix{Clarify that the version of the library which was used to report the bug is also included in the requirements.txt file}
+  \item Identify the version of the library used to report the bug along with other dependencies;
+  \item Write a \CodeIn{requirements.txt} file with the list of dependencies to reproduce the bug;
   \item Create a file showing the code that causes the bug (for documentation);
@@
 
+\subsection{Contribution}
+
+\tname\ allows users to contribute to the dataset by adding new bug
+instances. This opens up the tool to the community to help in
+expanding the dataset and improving the quality of the dataset.
+The following steps show how to contribute a new bug
+instance:
+
+\begin{enumerate}[leftmargin=0.5cm]
+  \item Identify issues in the issue tracker of the library of interest;
+  \item Create an issue in the repository of \tname\ with the template
+    "Reproduce Bug" (available in the repository);
+  \item Create a branch linked to the issue;
+  \item Add a self-contained bug reproduction script in a sub-directory
+    named with the GitHub issue identifier under the directory of the library;
+  \item Prepare the execution environment (Docker containers~\cite{merkel2014docker} for CUDA-dependent
+    bugs, \CodeIn{Conda Enviroment}~\cite{venv} for others);
+  \item Follow the steps in \ref{sec:method} to create the bug reproduction script;
+  \item Update the spreadsheets of the library with bug details;
+  \item Create a pull request to the main branch.
+\end{enumerate}
+
+\Fix{Abid: Added, please revise}
+
 \section{\tname: Use cases}

### 2025-03-20 paper/main.tex
Tool availability placeholder
Added stats about bug type

@@
 
+\Fix{Add a "Tool availablity" section and move the details there, upload the video to YouTube, archive 
+the tool at zenodo}
+
 We present \tname, a database of curated reproducible bugs to
@@
 for each kind of build, and column ``environment'' shows the breakdown
-of instances for each kind of environment to reproduce the bug.
+of instances for each kind of environment to reproduce the bug. Co-incidentally,
+all bugs that require a GPU build are reproduced using a docker
+container i.e. the column venv-docker is the same as bugs reproducible with CPU-GPU builds
+of the libraries respectively. Table~\ref{table:bug-stats} shows whay type of error is manifested
+due to each bug instance. In total, we have 15 different types of bug manifestations across
+the three libraries.
+
+\Fix{Added table and description, please revise}
 
@@
 been filtered with each criterion. Please review and revise}
+
+\begin{table}
+  \centering
+  \caption{\label{table:bug-stats}Different bug manifestation types from \tname.}
+  \begin{tabular}{lrrrr}\toprule
+    Bug manifestation type &Jax &Pytorch &Tensorflow \\\midrule
+    Internal Exception &11 &9 &1 \\
+    Incorrect Output &14 &11 &5 \\
+    Value Error &7 &0 &3 \\
+    Type Error &3 &2 &3 \\
+    Attribute Error &2 &0 &0 \\
+    Index Error &2 &1 &0 \\
+    Floating Point Error &1 &0 &0 \\
+    Error Not Raised &1 &0 &0 \\
+    Parse Error &1 &0 &0 \\
+    Runtime Error &1 &7 &1 \\
+    Not Implemented Error &1 &0 &0 \\
+    Memory Error &1 &1 &0 \\
+    Invalid Argument Error &1 &0 &1 \\
+    Crash &0 &4 &10 \\
+    Assertion Error &0 &2 &0 \\
+    \midrule
+    $\Sigma$ &46 &37 &24 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 

### 2025-03-20 paper/main.tex
left comment

@@
   problem have been proposed, but the lack of a curated set of
-  reproducible bugs in DL libraries hinders credible evaluation of these
-  techniques. We present \tname, a database of curated reproducible
-  bugs to fill that gap.
+  reproducible bugs in DL libraries hinders credible evaluation of
+  these techniques. We present \tname, a database of curated
+  reproducible bugs to fill that gap. Unique challenges exist in this
+  context, such as installing drivers of specific CUDA versions to
+  reproduce certain GPU-related bugs.
   %% enable credible  evaluation of bug-finding DL library testing techniques.
@@
 \Fix{What evaluation can be added to this section?}
-\subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}
+\subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}\label{sec:running-free-fuzz}
 
@@
 % \Fix{Consider the comments from Saikat, please.}
-Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug.
-Then it proceeds to run the entire testing tool on the enviroment.
-After the execution completes, the output can be checked for all failures produced by FreeFuzz (saved inside the container) and manually inspected to see if any failure that can reveal the bug in question was generated by the tool.
-In this case, the failure generated by FreeFuzz could not generate a failure that can reveal this bug since the API "torch.\_dynamo.export" is not supported by FreeFuzz.
+Initially, the script reproduces the bug and updates the environment
+inside the docker container of FreeFuzz to match the enviroment of the
+bug. Then, it proceeds to run the entire testing tool on the
+enviroment.
+
+\Fix{Abid, this does not make sense to me. If you are checking this
+  manually, you could run FreeFuzz separately and check manually. What
+  is the point?! You need to provide a list of bugs and check
+  automatically how many the tool can find (based on some criteria,
+  e.g, match the error message in Assertion or some n frames in the
+  stack (for crash)). --Marcelo}
+After the execution completes, the output can be
+checked for all failures produced by FreeFuzz (saved inside the
+container) and manually inspected to see if any failure that can
+reveal the bug in question was generated by the tool. In this case,
+the failure generated by FreeFuzz could not generate a failure that
+can reveal this bug since the API "torch.\_dynamo.export" is not
+supported by FreeFuzz.
 
@@
 
-\Fix{Abid: Added, please revise}
+%% \Fix{Abid: Added, please revise}
+%% \section{Use case: Evaluation of testing techniques}
+%% The primary use case of \tname\ is the evaluation of testing
+%% techniques. Dozens of API- and model-level testing techniques have
+%% been proposed in the literature recently and it is imperative to
+%% evaluate them using a standard
+%% benchmark. Section~\ref{sec:running-free-fuzz} elaborates on how to
+%% integrate a testing tool, such as FreeFuzz~\cite{wei2022free}, into
+%% \tname.
 
-\section{\tname: Use cases}
-
-We anticipate two major use cases for \tname: (1) \textbf{evaluation
-  of testing techniques} and (2) \textbf{evaluation of repair
-  techniques}. Dozens of API- and model-level testing techniques have
-been proposed in the literature recently and it is imperative to
-evaluate them using a standard benchmark. \tname\ provides such
-benchmark. Considering repair, as testing techniques mature it becomes
-important to identify candidate repairs that can be recommended to
-developers when reporting issues in bug trackers. With \tname\ it is
-possible to identify if the problem has been resolved. 
-\Fix{The concept of repairing has not been tied to any commands in the tool. Suggestions include
-a way to recreate an enviroment with the bug fixed, or a way to check if the bug has been fixed in a new version of the library.}
+%% We anticipate two major use cases for \tname: (1) \textbf{} and (2) \textbf{evaluation of repair
+%%   techniques}. Considering repair, as testing techniques mature it becomes
+%% important to identify candidate repairs that can be recommended to
+%% developers when reporting issues in bug trackers. With \tname\ it is
+%% possible to identify if the problem has been resolved. 
+%% \Fix{The concept of repairing has not been tied to any commands in the tool. Suggestions include
+%% a way to recreate an enviroment with the bug fixed, or a way to check if the bug has been fixed in a new version of the library.}
 

### 2025-03-20 paper/main.tex
Updated bug types

@@
 of the libraries respectively. Table~\ref{table:bug-stats} shows whay type of error is manifested
-due to each bug instance. In total, we have 15 different types of bug manifestations across
+due to each bug instance. In total, we have \numbugtypes\ different types of bug manifestations across
 the three libraries.
@@
 enviroment detailed in the report, we choose the bug to be included in
-our dataset. Through this process, we end up with \numtorchselected{},
-\numtfselected{}, and \numjaxselected{} bug instances for \torch, \tf,
+our dataset. Through this process, we end up with \numtorchbugs{},
+\numtfbugs{}, and \numjaxbugs{} bug instances for \torch, \tf,
 and \jax, respectively.
@@
     Bug manifestation type &Jax &Pytorch &Tensorflow \\\midrule
-    Internal Exception &11 &9 &1 \\
     Incorrect Output &14 &11 &5 \\
-    Value Error &7 &0 &3 \\
+    Internal Exception &11 &9 &4 \\
+    Value Error &7 &0 &4 \\
     Type Error &3 &2 &3 \\
-    Attribute Error &2 &0 &0 \\
+    Attribute Error &2 &0 &2 \\
     Index Error &2 &1 &0 \\
@@
     Parse Error &1 &0 &0 \\
-    Runtime Error &1 &7 &1 \\
+    Runtime Warning &1 &0 &0 \\
     Not Implemented Error &1 &0 &0 \\
@@
     Invalid Argument Error &1 &0 &1 \\
-    Crash &0 &4 &10 \\
+    Runtime Error &0 &7 &1 \\
     Assertion Error &0 &2 &0 \\
+    Segmentation Fault &0 &2 &1 \\
+    Floating Point Exception &0 &1 &0 \\
+    Aborted &0 &1 &8 \\
     \midrule
-    $\Sigma$ &46 &37 &24 \\
+    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} \\
     \bottomrule

### 2025-03-20 framework/stats.py

@@ -124,7 +124,7 @@ def process_file(libname, print_fmt, total_bugs):
         bug_manifest_type = dict(sorted(bug_manifest_type.items(), key=lambda item: item[1], reverse=True)) # sort by number of occurance
         for bug_m_type in bug_manifest_type.keys():
             if bug_m_type.strip() > "":
-                print(f'    {bug_m_type}: {bug_manifest_type[bug_m_type]}')
+                print(f'    {bug_m_type.title()}: {bug_manifest_type[bug_m_type]}')
             else:
                 print(f'    <undefined>: {bug_manifest_type[bug_m_type]}')
         print('----------------------------')

### 2025-03-20 paper/main.tex
Added tool availability from Intro to a new section

@@
 
-\Fix{Add a "Tool availablity" section and move the details there, upload the video to YouTube, archive 
-the tool at zenodo}
+% \Fix{Add a "Tool availablity" section and move the details there, upload the video to YouTube, archive 
+% the tool at zenodo}
 
@@
 equipped with a command-line interface to enable researchers to analyze
-and reproduce bug instances. The following screencast demonstrates some
-of the features of \tname:
-
-\url{https://tinyurl.com/BugsInDLLs}\\
+and reproduce bug instances.
 
@@
 two PhD students, and two faculty were involved in the work during
-this period. \tname\ is publicly available from the following URL:
-
-\url{https://github.com/ncsu-swat/bugsindlls}
+this period. Details on tool availability is provided in
+Section~\ref{sec:tool-availability}.
 
 \Fix{Need to add text regarding differentiating the tool from BugsInPy}
+
+\section{Tool Availability}
+\label{sec:tool-availability}
+\tname\ is publicly available from the following URL:
+
+\url{https://github.com/ncsu-swat/bugsindlls}\\
+
+The following screencast demonstrates some
+of the features of \tname:
+
+\url{https://tinyurl.com/BugsInDLLs}\\
+\Fix{Upload to YouTube with voiceover and add link here, archive 
+the tool at zenodo}
 

### 2025-03-21 framework/retrieve.py
Added preprocess and postprocess files

@@ -1,0 +1,22 @@
+import sys, os, csv
+
+def main():
+    if len(sys.argv) < 3:
+        print("Usage: python retrieve.py <colname> <library_name> <version>")
+        return
+    
+    colname = sys.argv[1]
+    libname = sys.argv[2]
+    version = sys.argv[3]
+    
+    dir_path = os.path.dirname(os.path.realpath(__file__))
+    with open(f'{dir_path}/../bug_dataset_{libname}.csv', mode='r') as csv_file:
+        csv_reader = csv.DictReader(filter(lambda row: not row.startswith(",Filter"), csv_file))
+        for row in csv_reader:
+            if row["Reproduced"] == "Yes":
+                if row["Buggy Version"].strip() == version.strip():
+                    print(row[colname])
+    
+
+if __name__ == "__main__":
+    main()

### 2025-03-21 tool-integration/FreeFuzz/postprocess.py

@@ -1,0 +1,99 @@
+import sys
+import os
+import subprocess
+from rapidfuzz import fuzz
+
+def main():
+    if len(sys.argv) < 2:
+        print("Usage: python match_bugs.py <config_name>")
+        return
+    config_name = sys.argv[1]
+
+    config_file = f"src/config/{config_name}"
+
+    library_name = None
+    output = None
+
+    with open(config_file, 'r') as file:
+        config_data = file.read()
+        for line in config_data.splitlines():
+            if line.startswith("libs"):
+                library_name = line.split('=')[1].strip()
+            elif library_name is not None and line.startswith(f"{library_name}_output"):
+                output = line.split('=')[1].strip()
+                break
+
+    output_folder = f"src/{output}"
+
+    with open("/tmp/apis_under_test.txt", 'r') as file:
+        apis_under_test = file.read().splitlines()
+
+    output_msgs = {}
+    for api in apis_under_test:
+        output_msgs[api] = ""
+
+    oracles = [name for name in os.listdir(output_folder) if os.path.isdir(os.path.join(output_folder, name))]
+    
+    print('\n')
+    
+    for oracle in oracles:
+        categories = [name for name in os.listdir(f"{output_folder}/{oracle}") if os.path.isdir(os.path.join(f"{output_folder}/{oracle}", name))]
+        for category in categories:
+            if category.endswith("bug"):
+                apis_under_category = [name for name in os.listdir(f"{output_folder}/{oracle}/{category}") if os.path.isdir(os.path.join(f"{output_folder}/{oracle}/{category}", name))]
+                if len(apis_under_category) == 0:
+                    print(f"No violation of {oracle} in the {category} category")
+                for api in apis_under_category:
+                    python_scripts = os.listdir(f"{output_folder}/{oracle}/{category}/{api}")
+                    if len(python_scripts) == 0:
+                        print(f"{api}: No violation of {oracle} in the {category} category")
+                    for script in python_scripts:
+                        # execute each script, store the output
+                        script_path = os.path.join(output_folder, oracle, category, api, script)
+                        result = subprocess.run(['python', script_path], capture_output=True, text=True)
+                        # print(f"Output of {script_path}:\n{result.stdout}")
+                        # if result.stderr:
+                        #     print(f"Error in {script_path}:\n{result.stderr}")
+                        output_msgs[api] += result.stdout + '\n'
+                        if result.stderr:
+                            output_msgs[api] += result.stderr + '\n'
+    
+    print('\n')
[…]

### 2025-03-21 tool-integration/FreeFuzz/preprocess.py

@@ -1,0 +1,36 @@
+import sys
+import os
+import subprocess
+
+def main():
+    if len(sys.argv) < 2:
+        print("Usage: python preprocess.py <library_name>")
+        return
+    library_name = sys.argv[1]
+    apis_file = f"data/{library_name}_APIdef.txt"
+    supported_apis = []
+
+    with open(apis_file, 'r') as file:
+        apis = file.read()
+
+        for api in apis.splitlines():
+            supported_apis.append(api.split("(")[0].strip())
+
+    with open("/tmp/apis_under_test.txt", 'r') as file:
+        apis_text = file.read()
+        print(f"\nAPIs under test:\n{apis_text}\n")
+        apis_under_test = apis_text.splitlines()
+
+    apis_to_skip = []
+    
+    for api in supported_apis:
+        if api not in apis_under_test:
+            apis_to_skip.append(api)        
+
+    skip_filename = f"src/config/skip_{library_name}.txt"
+    with open(skip_filename, 'w') as file:
+        for api in apis_to_skip:
+            file.write(api + '\n')
+
+if __name__ == "__main__":
+    main()

### 2025-03-21 tool-integration/FreeFuzz/run_freefuzz_docker.sh

@@ -3,9 +3,9 @@
 libname=${1:-torch}
 
 if [[ "$libname" == "torch" ]] || [[ "$libname" == "pytorch" ]]; then
-    docker exec -it freefuzz bash -c "cd src && python3 FreeFuzz.py --conf demo_torch.conf"
+    docker exec -it freefuzz bash -c "python3 preprocess.py torch && cd src && python3 FreeFuzz.py --conf demo_torch.conf && cd .. && python3 postprocess.py demo_torch.conf"
 elif [[ "$libname" == "tensorflow" ]] || [[ "$libname" == "tf" ]]; then
-    docker exec -it freefuzz bash -c "cd src && python3 FreeFuzz.py --conf demo_tf.conf"
+    docker exec -it freefuzz bash -c "python3 preprocess.py tf && cd src && python3 FreeFuzz.py --conf demo_tf.conf && cd .. && python3 postprocess.py demo_tf.conf"
 else
     echo "$libname not supported"
 fi

### 2025-03-21 paper/main.tex
pass on intro

@@
 
-\sloppy Serveral important application domains (e.g., transportation,
-medicine, etc.) use AI as part of their business processes. Deep
-Learning~(DL) libraries, such as \jax, \torch{}, and \tf{}, provide
-the building blocks for the AI components of these applications.
-Unfortunately, as any piece of software, these libraries contain
-bugs. An impressive number of techniques have been recently proposed
-to find bugs in these
+\sloppy Several application domains (e.g., transportation and
+medicine) use AI as part of their solutions. Deep Learning~(DL)
+libraries, such as \jax, \torch{}, and \tf{}, provide the building
+blocks for the AI components of these applications.  Unfortunately, as
+any piece of software, these libraries contain bugs. An impressive
+number of techniques have been recently proposed to find bugs in these
 libraries~\cite{wei2022free,xie2022docter,deng2022fuzzing,pham2019cradle,guo2020audee,wang2020deep,gu2022muffin,deng2023large,liu2023nnsmith,liu2023neuri,shi2023acetest,deng2023largeedge},
-however we observe that the evaluation of these techniques do
-\emph{not} use a reference set of reproducible bugs to evaluate their
-effectiveness. The lack of evaluation standards is an obstacle to the
-fair comparison of techniques, hindering research progress.
-\Fix{Clarify how the "evaluation set" used by the existing works is different from the "reference set" that we are proposing. Also, need more compelling reason/some sort of evaluation of other fuzzers
-to complement the motivation}
+however we observe these techniques propose an independent evaluation
+methodology. These techniques do \emph{not} use a reference database
+of reproducible bugs to evaluate their effectiveness. The lack of an
+evaluation standards is a serious obstacle to a fair and rigorous
+comparison of techniques and hinders research progress.
+
+%%~\cite{just2014defects4j,smytzek2024tests4py,widyasari2020bugsinpy,kim2021denchmark}
+Although many datasets of reproducible bugs have been proposed in the
+literature, there is a lack of solutions satisfying the following
+criteria:
+
+\begin{enumerate}[leftmargin=0.2in]
+\item developers should be able to write tests scripts in Python;
+\item ~they should be able to handle nighly builds and specific
+  versions of CUDA (\textsection~\ref{sec:challenges});
+\item they should be able to integrate fuzzing tools in the framework.
+\end{enumerate}
+
+Note that DL libraries are written in Python. Existing datasets of
+reproducible bugs exist in Python (e.g.,
+BugInPy~\cite{widyasari2020bugsinpy} and
+Tests4Py~\cite{smytzek2024tests4py}), but they fail to satisfy the
+second or the third requirement. For example, BugsInPy and Tests4Py do
+not support artifacts in Docker, which are necessary to modify CUDA
+drivers in the guest OS to reproduce specific GPU-related
+bugs.\footnote{BugsInPy and Tests4Py use python virtual environments,
+e.g., venv and pyenv.} More importantly, a dataset of Deep Learning
+Libraries needs to support the integration of new fuzzing tools. The
+central purpose of such dataset is to \emph{enable the systematic
+evaluation of testing techniques}.
+
+%% \Fix{Clarify how the
+%%   "evaluation set" used by the existing works is different from the
+%%   "reference set" that we are proposing. Also, need more compelling
+%%   reason/some sort of evaluation of other fuzzers to complement the
+%%   motivation}
 
@@
 
-We present \tname, a database of curated reproducible bugs to
-enable credible evaluation of DL library testing techniques. \tname\ is
-equipped with a command-line interface to enable researchers to analyze
-and reproduce bug instances.
+We present \tname, a database of curated reproducible bugs to enable
+credible evaluation of DL library testing techniques. \tname\ is
+equipped with a command-line interface to enable researchers to
+analyze and reproduce bug instances.  \tname\ has been under active
+development since March 21, 2024, the day of the first commit in its
+GitHub repository. Two UROP students, two PhD students, and two
+faculty were involved in the work during this
+period. Section~\ref{sec:tool-availability} details tool availability.
 
-\tname\ has been under active development since March 21, 2024, the
-day of the first commit in its GitHub repository. Two UROP students,
-two PhD students, and two faculty were involved in the work during
-this period. Details on tool availability is provided in
-Section~\ref{sec:tool-availability}.
-
-\Fix{Need to add text regarding differentiating the tool from BugsInPy}
+%\Fix{Need to add text regarding differentiating the tool from BugsInPy}
 

### 2025-03-21 paper/main.tex
pass on section 3

@@
 \affiliation{%
-  \institution{NC State University}
+  \institution{NC State University, USA}
   %\city{Rocquencourt}
-  \country{USA}
+  \country{}
 }
@@
 \affiliation{%
- \institution{Amrita Vishwa Vidyapeetham}
+ \institution{Amrita Vishwa Vidyapeetham, India}
  %% \city{Doimukh}
  %% \state{Arunachal Pradesh}
- \country{India}}
+ \country{}
+}
 \email{amanks@am.amrita.edu}
@@
 \affiliation{%
- \institution{NC State University}
+ \institution{NC State University, USA}
  %% \city{Doimukh}
  %% \state{Arunachal Pradesh}
- \country{USA}}
+ \country{}
+}
 \email{fqin2@ncsu.edu}
@@
 \affiliation{%
- \institution{Purdue University}
+ \institution{Purdue University, USA}
  %% \city{Doimukh}
  %% \state{Arunachal Pradesh}
- \country{USA}}
+ \country{}
+}
 \email{wu2059@purdue.edu}
@@
 \affiliation{%
- \institution{Cornell University}
+ \institution{Cornell University, USA}
  %% \city{Doimukh}
  %% \state{Arunachal Pradesh}
- \country{USA}}
+ \country{}
+}
 \email{saikatd@cornell.edu}
@@
 \affiliation{%
- \institution{NC State University}
+ \institution{NC State University, USA}
  %% \city{Doimukh}
  %% \state{Arunachal Pradesh}
- \country{USA}}
+ \country{}
+}
 \email{mdamori@ncsu.edu}
@@
 of bug instances, column ``build'' shows the breakdown of instances
-for each kind of build, and column ``environment'' shows the breakdown
-of instances for each kind of environment to reproduce the bug. Co-incidentally,
+for each kind of build (release or nightly), and column
+``environment'' shows the breakdown of instances for each kind of
+environment to reproduce the bug (venv or docker). Co-incidentally,
 all bugs that require a GPU build are reproduced using a docker
-container i.e. the column venv-docker is the same as bugs reproducible with CPU-GPU builds
-of the libraries respectively. Table~\ref{table:bug-stats} shows whay type of error is manifested
-due to each bug instance. In total, we have \numbugtypes\ different types of bug manifestations across
-the three libraries.
-
-\Fix{Added table and description, please revise}
+container, i.e. the column venv-docker matches would have been
+observed with a column CPU-GPU, to indicate if the bug is can be
+reproduced with a CPU or if it requires a
+GPU. Table~\ref{table:bug-stats} shows the breakdown error types for
+the bugs in our dataset. The row ``Incorrect Output'' is listed first
+as it requires a distinct kind of oracle comparing consistency of the
+outputs of test runs on a CPU and on GPU. In total, we have
+\numbugtypes\ different types of bug manifestations across the three
+libraries.
 
@@
 of issues due to a lack of a label for bugs in the issue tracker.
-
-We then manually inspect the
-filtered issues to ensure that they contain enough information to
-reproduce the bug, i.e.,
-code to reproduce the bug, dependencies required for the bug
-reproduction, clear description of the desired behavior,
-etc. We also filter bugs that are not in the core functionality
-of the library e.g. documentation issues, feature requests, etc.
-After this stage of manual inspection, we end up with \numtorchinspected{}
-issues for \torch, \numtfinspected{} issues for \tf, and \numjaxinspected{}
-issues for \jax.
+%%
+Then, we manually inspect the filtered issues to ensure that they
+contain enough information to reproduce the bug, i.e., code to
+reproduce the bug, dependencies required for the bug reproduction,
+clear description of the desired behavior, etc. We discard bugs that
+are not in the core functionality of the library e.g. documentation
+issues, feature requests, etc. After this stage of manual inspection,
+we end up with \numtorchinspected{} issues for \torch,
+\numtfinspected{} issues for \tf, and \numjaxinspected{} issues for
+\jax.
+%
+Finally, we assess the reproducibility of the bug by creating a
+virtual environment that contains the necessary dependencies to
+reproduce the bug.  Once we can successfully reproduce the bug by
+creating the enviroment detailed in the report, we include the
+corresponding artifacts in our dataset. Throughout this process, we
+obtain \textbf{\numjaxbugs{}}, \textbf{\numtorchbugs{}}, and
+\textbf{\numtfbugs{}} bug instances for \jax, \torch, and \tf,
+respectively.
 
@@
 % etc.
-Afterwards, we assess the reproducibility of the bug by creating a
-virtual environment that contains the necessary dependencies to
-reproduce the bug.
-Once we can successfully reproduce the bug by creating the
-enviroment detailed in the report, we choose the bug to be included in
-our dataset. Through this process, we end up with \numtorchbugs{},
-\numtfbugs{}, and \numjaxbugs{} bug instances for \torch, \tf,
-and \jax, respectively.
 
-\Fix{Abid: Added what labels were used, which period we took the issues from,
-how many issues we looked at, defined "bug reports", mentioned how many bugs had 
-been filtered with each criterion. Please review and revise}
+%% \Fix{Abid: Added what labels were used, which period we took the issues from,
+%% how many issues we looked at, defined "bug reports", mentioned how many bugs had 
+%% been filtered with each criterion. Please review and revise}
 
@@
   \centering
-  \caption{\label{table:bug-stats}Different bug manifestation types from \tname.}
+  \caption{\label{table:bug-stats}Different bug manifestation types
+    from \tname.\Fix{If time allows, add a total column and sort rows
+      according to it (except incorrect output)}}
   \begin{tabular}{lrrrr}\toprule
@@
 
-\textbf{Handling bugs in specific GPU-CUDA versions requires OS
-  changes:} Some GPU-related bug instances can only be reproduced with
-specific versions of CUDA~\cite{cuda}, NVIDIA's platform and API for
-programming GPUs. These instances require specific CUDA drivers to be
-installed on the system. Python virtual enviroments are not designed
-to enable change of OS drivers.
+\vspace{0.5ex}\noindent\textbf{Handling bugs in specific GPU-CUDA
+  versions requires OS changes:} Some GPU-related bug instances can
+only be reproduced with specific versions of CUDA~\cite{cuda},
+NVIDIA's platform and API for programming GPUs. These instances
+require specific CUDA drivers to be installed on the system. Python
+virtual enviroments are not designed to enable change of OS drivers.
 % GPU builds\Fix{I don't understance GPU builds. do you mean
@@
 %   space, show only directory with files and the test case. - Abid: by the test case, do you mean the python code used to reproduce the bug?} 
-  The issue no. 120903 in pytorch has the following test code that checks the oracle:
+  The issue no. 120903 in \torch\ has the following test code that checks the oracle:
 

### 2025-03-21 paper/main.tex
adding short title and page number

@@
 
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-\title{\tname: A Database of Reproducible Bugs in Deep
-  Learning Libraries to Enable Systematic Evaluation of Testing
-  Techniques}
+%% The "title" command has an optional parameter, allowing the author
+%% to define a "short title" to be used in page headers.
+
+\newcommand{\myshort}{\tname~: A Database of Reproducible Bugs in
+  Deep Learning Libraries}
+
+\title[\myshort{}]{\myshort{} to Enable Systematic Evaluation of
+  Testing Techniques}
 
@@
 \maketitle
+%% add page numbers
+\pagestyle{plain}
 

### 2025-03-21 paper/main.tex
Added text about tool integration

@@
 platform linux -- Python 3.10.0, pytest-8.2.0, pluggy-1.5.0
-rootdir: /home/mnaziri/Documents/DL_Testing/dnnbugs/pytorch/issue_120903
-collected 1 item
-
+...
 test_issue_120903.py Pytorch issue no. 120903
@@
 
-\Fix{What evaluation can be added to this section?}
+% \Fix{What evaluation can be added to this section?}
 \subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}\label{sec:running-free-fuzz}
 
-Tool execution proceeds in two steps: (1) Creation of Docker container
-associated with a tool and (2) Execution of the tool.  Let us
+To run any tool on \tname, a script that contains commands to run the tool, a preprocessing script to extract error types and buggy APIs for a specific library version, and a postprocessing script to match the execution log with the expected errors needs to be provided.
+We provide implementations for FreeFuzz~\cite{wei2022free} in the \CodeIn{tool-integration} directory that contains templates for these scripts.
+
+Tool execution proceeds in four steps: (1) Creation of Docker container
+associated with a tool, (2) Reproduce an example bug from the library version provided as input (3) Running a preprocessing script to extract error types and buggy APIs for a specific library vesion (4) Execution of the tool and (5) Running a postprocessing script to match the execution log with the expected errors.
+Let us
 demonstrate this process on FreeFuzz~\cite{wei2022free}, an API-level
@@
 of the two-step integration method.
-
-%i.e., it builds a Docker container for FreeFuzz:
-
-% \Fix{walkthrough an example. Show input and part of output. Explain
-%   the output.}
-%% The user needs to execute two steps to integrate a testing tool (e.g.,
-%% FreeFuzz) on \tname.
-%% 1. Create a docker container for the tool
-%% 2. A script that takes the name of the library as an argument and run FreeFuzz on the library
 
@@
 
-%\Fix{I am here -Marcelo}
-%% Once the docker container is built and is running, providing the name
-%% of the container and the location of the script that can execute the
-%% tool (either absolute path or relative to the root of the repository)
-%% to the command
-
-The second step runs the \tname's command \CodeIn{run-tool}, which
-proceeds in two steps (1) reproduce the bug separately, as done with
-command \CodeIn{run-test}, and (2) then update the environment inside
-the docker container of the tool to run the tool with the script
-provided. The first step is a sanity check to assure that the bug can
-indeed be reproduced. For example, the following command runs FreeFuzz
-on the enviroment of the bug associated with the issue 117033 from
-\torch.
+The next four steps are executed with \tname's command \CodeIn{run-tool}.
+When the comment is run, firstly an example bug that is reproducible with the library version provided as an input is run as a sanity check.
+Then, a preprocessing script to extract error types and buggy APIs for a specific library version runs.
+Then the environment inside
+the docker container of the tool is updated to match the library version passed as an input and the fuzzing tool runs inside the enviroment.
+After the execution is complete, the next step is running a postprocessing script that checks the execution log against the error types of the bug to determine if the bugs were reproduced or not.
+For example, the following command runs FreeFuzz
+on version 2.2.0 from \torch.
 
 \begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
-$> run-tool --container freefuzz --library-name pytorch --bug-id 117033 --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
+$> run-tool --container freefuzz --library-name pytorch \ 
+   --use-library-version 2.2.0 \
+   --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
 \end{lstlisting}
 
+The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
 The output looks like the following:
@@
 \begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
+Using bug-id 120903 for library pytorch version 2.2.0
 ...
-(*@\textbf{[Reproducing the bug]}@*)
 ====== test session starts ======
-platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
+platform linux -- Python 3.10.0, pytest-8.2.0, pluggy-1.5.0
 ...
-IndexError: list index out of range
+RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please report a bug to PyTorch.
 ====== 1 passed in 1.09s ======
 ...
-
-(*@\textbf{[Setting up FreeFuzz]}@*)
 Updating environment in the container of the testing tool
-Successfully copied 16.4kB to freefuzz:/tmp/issue_117033
-__pycache__  install_environment.sh  reproduce_bug.sh  requirements.txt  test_issue_117033.py
+Successfully copied 16.4kB to freefuzz:/tmp/issue_120903
 ...
-
-(*@\textbf{[Running FreeFuzz]}@*)
 Running the testing tool on the environment of the bug
+APIs under test:
+torch.fake_quantize_per_channel_affine
+torch.all
+torch.compile
 Testing on  ['torch']
-torch.log2
+torch.atanh
 ...
-torch.nn.MaxUnpool2d
-../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [1,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
-../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [2,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
-...
+No violation of precision-oracle in the compare-bug category
+No violation of precision-oracle in the potential-bug category
+No violation of cuda-oracle in the compare-bug category
+No violation of cuda-oracle in the potential-bug category
+No violation of crash-oracle in the compare-bug category
+No violation of crash-oracle in the potential-bug category
+-> torch.fake_quantize_per_channel_affine did not face any failures
+-> torch.all did not face any failures
+-> torch.compile did not face any failures
+Reproduced 0 out of 3 bugs
 \end{lstlisting}
@@
 % \Fix{Consider the comments from Saikat, please.}
-Initially, the script reproduces the bug and updates the environment
-inside the docker container of FreeFuzz to match the enviroment of the
-bug. Then, it proceeds to run the entire testing tool on the
-enviroment.
+% Initially, the script reproduces the bug and updates the environment
+% inside the docker container of FreeFuzz to match the enviroment of the
+% bug. Then, it proceeds to run the entire testing tool on the
+% enviroment.
 
-\Fix{Abid, this does not make sense to me. If you are checking this
-  manually, you could run FreeFuzz separately and check manually. What
-  is the point?! You need to provide a list of bugs and check
-  automatically how many the tool can find (based on some criteria,
-  e.g, match the error message in Assertion or some n frames in the
-  stack (for crash)). --Marcelo}
+% \Fix{Abid, this does not make sense to me. If you are checking this
+%   manually, you could run FreeFuzz separately and check manually. What
+%   is the point?! You need to provide a list of bugs and check
+%   automatically how many the tool can find (based on some criteria,
+%   e.g, match the error message in Assertion or some n frames in the
+%   stack (for crash)). --Marcelo}
 After the execution completes, the output can be
@@
 supported by FreeFuzz.
+
+The execution log shows that the tool did not reproduce any of the
+three bugs that were expected to be reproduced since the three buggy APIs \CodeIn{torch.fake\_quantize\_per\_channel\_affine}, \CodeIn{torch.all}, and \CodeIn{torch.compile} are not supported by FreeFuzz.
+The outputs of the tool are saved in the container and can be inspected manually to further inspect the execution log.
 

### 2025-03-21 paper/main.tex
Added total column

@@
   \caption{\label{table:bug-stats}Different bug manifestation types
-    from \tname.\Fix{If time allows, add a total column and sort rows
-      according to it (except incorrect output)}}
-  \begin{tabular}{lrrrr}\toprule
-    Bug manifestation type &Jax &Pytorch &Tensorflow \\\midrule
-    Incorrect Output &14 &11 &5 \\
-    Internal Exception &11 &9 &4 \\
-    Value Error &7 &0 &4 \\
-    Type Error &3 &2 &3 \\
-    Attribute Error &2 &0 &2 \\
-    Index Error &2 &1 &0 \\
-    Floating Point Error &1 &0 &0 \\
-    Error Not Raised &1 &0 &0 \\
-    Parse Error &1 &0 &0 \\
-    Runtime Warning &1 &0 &0 \\
-    Not Implemented Error &1 &0 &0 \\
-    Memory Error &1 &1 &0 \\
-    Invalid Argument Error &1 &0 &1 \\
-    Runtime Error &0 &7 &1 \\
-    Assertion Error &0 &2 &0 \\
-    Segmentation Fault &0 &2 &1 \\
-    Floating Point Exception &0 &1 &0 \\
-    Aborted &0 &1 &8 \\
+    from \tname.}
+  \begin{tabular}{lrrrrr}\toprule
+    Bug manifestation type &Jax &Pytorch &Tensorflow &Total \\\midrule
+    Incorrect Output &14 &11 &5 &30 \\
+    Internal Exception &11 &9 &4 &24 \\
+    Value Error &7 &0 &4 &11 \\
+    Type Error &0 &1 &8 &9 \\
+    Attribute Error &3 &2 &3 &8 \\
+    Index Error &0 &7 &1 &8 \\
+    Runtime Error &2 &0 &2 &4 \\
+    Memory Error &2 &1 &0 &3 \\
+    Invalid Argument Error &0 &2 &1 &3 \\
+    Floating Point Error &1 &1 &0 &2 \\
+    Error Not Raised &1 &0 &1 &2 \\
+    Parse Error &0 &2 &0 &2 \\
+    Runtime Warning &1 &0 &0 &1 \\
+    Not Implemented Error &1 &0 &0 &1 \\
+    Assertion Error &1 &0 &0 &1 \\
+    Segmentation Fault &1 &0 &0 &1 \\
+    Floating Point Exception &1 &0 &0 &1 \\
+    Aborted &0 &1 &0 &1 \\
     \midrule
-    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} \\
+    $\Sigma$ &\numjaxbugs{} &\numtorchbugs{} &\numtfbugs{} &\numbugs{} \\
     \bottomrule

### 2025-03-21 paper/main.tex
minor

@@
 
-To run any tool on \tname, a script that contains commands to run the tool, a preprocessing script to extract error types and buggy APIs for a specific library version, and a postprocessing script to match the execution log with the expected errors needs to be provided.
-We provide implementations for FreeFuzz~\cite{wei2022free} in the \CodeIn{tool-integration} directory that contains templates for these scripts.
+A developer needs to provide three scripts to integrate a fuzzing
+tool: (1) a script that contains commands to run the tool; (2) a
+preprocessing script to extract error types and buggy APIs for a
+specific library version, and (3) a postprocessing script to match the
+execution log with the expected errors needs to be provided. The
+directory \CodeIn{tool-integration} that contains templates for these
+scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
+popular API fuzzer for DL libraries.
+%
+%% Tool execution proceeds in four steps: (1) Creation of Docker
+%% container associated with a tool, (2) Reproduction of example bug from
+%% the library version provided as input (3) Execution of preprocessing
+%% script to extract error types and buggy APIs for a specific library
+%% vesion (4) Execution of the tool and (5) Execution of postprocessing
+%% script to match the execution log with the expected errors.
 
-Tool execution proceeds in four steps: (1) Creation of Docker container
-associated with a tool, (2) Reproduce an example bug from the library version provided as input (3) Running a preprocessing script to extract error types and buggy APIs for a specific library vesion (4) Execution of the tool and (5) Running a postprocessing script to match the execution log with the expected errors.
-Let us
-demonstrate this process on FreeFuzz~\cite{wei2022free}, an API-level
-fuzzer for DL libraries. The following script executes the first step
-of the two-step integration method.
+We demonstrate the integration of FreeFuzz~\cite{wei2022free}. The
+following script creates a Docker container associated with FreeFuzz.
 
@@
 The script \CodeIn{install\_freefuzz\_docker.sh} contains the
-following instructions:
+following instructions\Fix{add brief explanation for what it does}:
 
@@
 
-The next four steps are executed with \tname's command \CodeIn{run-tool}.
-When the comment is run, firstly an example bug that is reproducible with the library version provided as an input is run as a sanity check.
+The next four steps are executed with \tname's command
+\CodeIn{run-tool}.
+
+When the command is run, firstly an example bug that is reproducible with the library version provided as an input is run as a sanity check.
 Then, a preprocessing script to extract error types and buggy APIs for a specific library version runs.

### 2025-03-21 paper/main.tex
comments

@@
 specific library version, and (3) a postprocessing script to match the
-execution log with the expected errors needs to be provided. The
+execution log with the expected errors needs to be provided.\Fix{name
+  these scripts here and refer back to them in the text below} The
 directory \CodeIn{tool-integration} that contains templates for these
@@
 popular API fuzzer for DL libraries.
-%
-%% Tool execution proceeds in four steps: (1) Creation of Docker
-%% container associated with a tool, (2) Reproduction of example bug from
-%% the library version provided as input (3) Execution of preprocessing
-%% script to extract error types and buggy APIs for a specific library
-%% vesion (4) Execution of the tool and (5) Execution of postprocessing
-%% script to match the execution log with the expected errors.
+
+\Fix{remove this paragraph. Explain the steps when they appear. It is difficult
+  to follow}
+Tool execution proceeds in four steps: (1) Creation of Docker
+container associated with a tool, (2) Reproduction of example bug from
+the library version provided as input (3) Execution of preprocessing
+script to extract error types and buggy APIs for a specific library
+vesion (4) Execution of the tool and (5) Execution of postprocessing
+script to match the execution log with the expected errors.\Fix{up to here}
 
@@
 The next four steps are executed with \tname's command
-\CodeIn{run-tool}.
+\CodeIn{run-tool}.\Fix{I don't know what are the four steps (I can't
+  remember anymore)}
 
-When the command is run, firstly an example bug that is reproducible with the library version provided as an input is run as a sanity check.
+\Fix{Can't you just explain what is the input-output and what it does
+  (at a very high level)?}When the command is run, firstly an example bug that is reproducible with the library version provided as an input is run as a sanity check.
 Then, a preprocessing script to extract error types and buggy APIs for a specific library version runs.
@@
 can reveal this bug since the API "torch.\_dynamo.export" is not
-supported by FreeFuzz.
+supported by FreeFuzz.\Fix{This is bad in two way: (1) we did not give
+  a chance to Freefuzz; unsupported API (2) it does not show any case
+  where the tool can reproduce the bug (and demo that our matchers
+  work). I hope you can do this on video or show another example to
+  complement this or modify this.}
 

### 2025-03-21 paper/main.tex
Updated text

--- 2025-03-21 paper/main.tex
@@
 
-The following screencast demonstrates some
+The following video demonstrates some
 of the features of \tname:
 
-\url{https://tinyurl.com/BugsInDLLs}\\
-\Fix{Upload to YouTube with voiceover and add link here, archive 
-the tool at zenodo}
+\url{https://www.youtube.com/watch?v=NslNWrULT1c}\\
+% \Fix{Upload to YouTube with voiceover and add link here, archive 
+% the tool at zenodo}
 
@@
 A developer needs to provide three scripts to integrate a fuzzing
-tool: (1) a script that contains commands to run the tool; (2) a
+tool: (1) a script that contains commands to run the tool (e.g. \CodeIn{run\_freefuzz\_docker.sh}); (2) a
 preprocessing script to extract error types and buggy APIs for a
-specific library version, and (3) a postprocessing script to match the
-execution log with the expected errors needs to be provided. The
+specific library version (\CodeIn{preprocess.py}), and (3) a postprocessing script to match the
+execution log with the expected errors (\CodeIn{postprocess.py}) needs to be provided.
+% \Fix{name
+%   these scripts here and refer back to them in the text below} 
+The
 directory \CodeIn{tool-integration} that contains templates for these
@@
 popular API fuzzer for DL libraries.
-%
-%% Tool execution proceeds in four steps: (1) Creation of Docker
-%% container associated with a tool, (2) Reproduction of example bug from
-%% the library version provided as input (3) Execution of preprocessing
-%% script to extract error types and buggy APIs for a specific library
-%% vesion (4) Execution of the tool and (5) Execution of postprocessing
-%% script to match the execution log with the expected errors.
+% \Fix{remove this paragraph. Explain the steps when they appear. It is difficult
+%   to follow}
+% \Fix{up to here}
 
@@
 \noindent
-The script \CodeIn{install\_freefuzz\_docker.sh} contains the
-following instructions\Fix{add brief explanation for what it does}:
+The script \CodeIn{install\_freefuzz\_docker.sh} build the docker container
+that contains the tool FreeFuzz. The script contains the
+following instructions:
+% \Fix{add brief explanation for what it does}:
 
@@
 
-The next four steps are executed with \tname's command
-\CodeIn{run-tool}.
+\Fix{Please revise}
+The command \CodeIn{run-tool} takes the library version as an input, along with the name of the docker container, the name of the library, and the script that contains the commands to run the tool (\CodeIn{run\_freefuzz\_docker.sh}) and it outputs how many bugs that are reproducible with this library version were successfully reproduced by a tool (e.g.
+FreeFuzz).
+Tool execution proceeds as following. First, creation of docker
+container associated with the tool done with the script \CodeIn{install\_freefuzz\_docker.sh}. 
+Then an example bug that is reproducible with the library version provided as an input is run as a sanity check. 
+Then the preprocessing
+script (\CodeIn{preprocess.py}) is executed to extract error types and buggy APIs for a specific library
+vesion. Then the environment inside
+the docker container of the tool is updated to match the library version passed as an input and the fuzzing tool runs inside the enviroment.
+After the execution is complete, the next step is running a postprocessing script (\CodeIn{postprocess.py}) that checks the execution log against the error types of the bug to determine if the bugs were reproduced or not.
 
-When the command is run, firstly an example bug that is reproducible with the library version provided as an input is run as a sanity check.
-Then, a preprocessing script to extract error types and buggy APIs for a specific library version runs.
-Then the environment inside
-the docker container of the tool is updated to match the library version passed as an input and the fuzzing tool runs inside the enviroment.
-After the execution is complete, the next step is running a postprocessing script that checks the execution log against the error types of the bug to determine if the bugs were reproduced or not.
 For example, the following command runs FreeFuzz
@@
 
-The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
+% The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
 The output looks like the following:
@@
 %   stack (for crash)). --Marcelo}
-After the execution completes, the output can be
-checked for all failures produced by FreeFuzz (saved inside the
-container) and manually inspected to see if any failure that can
-reveal the bug in question was generated by the tool. In this case,
-the failure generated by FreeFuzz could not generate a failure that
-can reveal this bug since the API "torch.\_dynamo.export" is not
-supported by FreeFuzz.
+% After the execution completes, the output can be
+% checked for all failures produced by FreeFuzz (saved inside the
+% container) and manually inspected to see if any failure that can
+% reveal the bug in question was generated by the tool. In this case,
+% the failure generated by FreeFuzz could not generate a failure that
+% can reveal this bug since the API "torch.\_dynamo.export" is not
+% supported by FreeFuzz.
+% \Fix{This is bad in two way: (1) we did not give
+%   a chance to Freefuzz; unsupported API (2) it does not show any case
+%   where the tool can reproduce the bug (and demo that our matchers
+%   work). I hope you can do this on video or show another example to
+%   complement this or modify this.}
+
+\Fix{Abid: Added text to motivate adding support for these APIs, please revise}
 
@@
 The outputs of the tool are saved in the container and can be inspected manually to further inspect the execution log.
+From this result, the developer can decide to add support for these three APIs in FreeFuzz and run the tool again to check if the bugs can be reproduced now.
+This will allow developers to decide on which APIs to add support for.
 

### 2025-03-21 paper/main.tex
comments

@@
 \noindent
-The script \CodeIn{install\_freefuzz\_docker.sh} build the docker container
-that contains the tool FreeFuzz. The script contains the
-following instructions:
-% \Fix{add brief explanation for what it does}:
+The script \CodeIn{install\_freefuzz\_docker.sh} build the docker
+container that encapsulates FreeFuzz.
 
-\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
-#!/bin/bash
-git clone https://github.com/ise-uiuc/FreeFuzz.git
-docker build -t freefuzz .
-docker run --name freefuzz --gpus all -d freefuzz:latest
-docker exec -it freefuzz mongorestore dump/
-\end{lstlisting}
+%% 
+%% The script contains the following instructions:
+%% % \Fix{add brief explanation for what it does}:
+%% \begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
+%% #!/bin/bash
+%% git clone https://github.com/ise-uiuc/FreeFuzz.git
+%% docker build -t freefuzz .
+%% docker run --name freefuzz --gpus all -d freefuzz:latest
+%% docker exec -it freefuzz mongorestore dump/
+%% \end{lstlisting}
 
-\Fix{Please revise}
-The command \CodeIn{run-tool} takes the library version as an input, along with the name of the docker container, the name of the library, and the script that contains the commands to run the tool (\CodeIn{run\_freefuzz\_docker.sh}) and it outputs how many bugs that are reproducible with this library version were successfully reproduced by a tool (e.g.
-FreeFuzz).
-Tool execution proceeds as following. First, creation of docker
-container associated with the tool done with the script \CodeIn{install\_freefuzz\_docker.sh}. 
-Then an example bug that is reproducible with the library version provided as an input is run as a sanity check. 
-Then the preprocessing
-script (\CodeIn{preprocess.py}) is executed to extract error types and buggy APIs for a specific library
-vesion. Then the environment inside
-the docker container of the tool is updated to match the library version passed as an input and the fuzzing tool runs inside the enviroment.
-After the execution is complete, the next step is running a postprocessing script (\CodeIn{postprocess.py}) that checks the execution log against the error types of the bug to determine if the bugs were reproduced or not.
-
-For example, the following command runs FreeFuzz
-on version 2.2.0 from \torch.
+The following script runs FreeFuzz all bugs associated with version
+2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
+version as an input, along with the name of the docker container
+(already created), the name of the library, and the user-provided
+script containing the commands to run the tool
+(\CodeIn{run\_freefuzz\_docker.sh}. The script reports on output how
+many bugs are reproducible with this library version were successfully
+reproduced by the given tool.  Tool execution proceeds as
+follows. First, creation of docker container associated with the tool
+done\Fix{ask gpt to revise/polish the text} with the script
+\CodeIn{install\_freefuzz\_docker.sh}.  Then, an example bug\Fix{I
+  don't understand ``example bug''. bugs in this version, no??!!} that
+is reproducible with the library version provided as an input is run
+as a sanity check.  Then, the preprocessing script
+(\CodeIn{preprocess.py}) is executed to extract error types and buggy
+APIs for a specific library vesion and the environment inside the
+docker container of the tool is updated to match the library version
+passed as an input and the fuzzing tool runs inside the
+enviroment. After the execution is complete, the script finally runs a
+postprocessing script (\CodeIn{postprocess.py}) to check the execution
+log against the ground truth to determine if the bugs were reproduced
+or not.
 

### 2025-03-21 paper/main.tex
Added DOI
Revised

@@
 
-\url{https://github.com/ncsu-swat/bugsindlls}\\
+\url{https://github.com/ncsu-swat/bugsindlls}
 
@@
 
-\url{https://www.youtube.com/watch?v=NslNWrULT1c}\\
+\url{https://www.youtube.com/watch?v=NslNWrULT1c}
+
+The archived version at Zenodo is available with this DOI:
+
+\url{https://doi.org/10.5281/zenodo.15064163}\\
+
 % \Fix{Upload to YouTube with voiceover and add link here, archive 
@@
 reproduced by the given tool.  Tool execution proceeds as
-follows. First, creation of docker container associated with the tool
-done\Fix{ask gpt to revise/polish the text} with the script
-\CodeIn{install\_freefuzz\_docker.sh}.  Then, an example bug\Fix{I
-  don't understand ``example bug''. bugs in this version, no??!!} that
-is reproducible with the library version provided as an input is run
-as a sanity check.  Then, the preprocessing script
-(\CodeIn{preprocess.py}) is executed to extract error types and buggy
-APIs for a specific library vesion and the environment inside the
-docker container of the tool is updated to match the library version
-passed as an input and the fuzzing tool runs inside the
-enviroment. After the execution is complete, the script finally runs a
-postprocessing script (\CodeIn{postprocess.py}) to check the execution
-log against the ground truth to determine if the bugs were reproduced
-or not.
+follows. First, a Docker container associated with the tool is created using
+\CodeIn{install_freefuzz_docker.sh}. Next, a reproducible bug is tested using
+the specified library version as input to verify the setup.
+Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
+to extract error types and identify buggy APIs for the given library version.
+The environment inside the Docker container is then updated to match the specified version, 
+ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
+script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
+determining whether the bugs were successfully reproduced.
 

### 2025-03-21 paper/main.tex
saving space

@@
 \documentclass[sigconf,screen]{acmart}
+
+\setcopyright{none} % to remove the copyright notice
+\settopmatter{printacmref=false} % to remove the ACM Reference Format
+\renewcommand\footnotetextcopyrightpermission[1]{} % to remove copyright box
 
@@
 %% complete the rights form.
-\setcopyright{acmlicensed}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{XXXXXXX.XXXXXXX}
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation email}{June 03--05,
-  2018}{Woodstock, NY}
-%%
-%%  Uncomment \acmBooktitle if the title of the proceedings is different
-%%  from ``Proceedings of ...''!
-%%
-%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-%%  June 03--05, 2018, Woodstock, NY}
-\acmISBN{978-1-4503-XXXX-X/2018/06}
-\acmBooktitle{Companion Proceedings of the 33rd ACM Symposium on the Foundations
-of Software Engineering (FSE '25), June 23--27, 2025, Trondheim, Norway}
+%% \setcopyright{acmlicensed}
+%% \copyrightyear{2018}
+%% \acmYear{2018}
+%% \acmDOI{XXXXXXX.XXXXXXX}
+%% %% These commands are for a PROCEEDINGS abstract or paper.
+%% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
+%%   conference title from your rights confirmation email}{June 03--05,
+%%   2018}{Woodstock, NY}
+%% %%
+%% %%  Uncomment \acmBooktitle if the title of the proceedings is different
+%% %%  from ``Proceedings of ...''!
+%% %%
+%% %%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
+%% %%  June 03--05, 2018, Woodstock, NY}
+%% \acmISBN{978-1-4503-XXXX-X/2018/06}
+%% \acmBooktitle{Companion Proceedings of the 33rd ACM Symposium on the Foundations
+%% of Software Engineering (FSE '25), June 23--27, 2025, Trondheim, Norway}
 
@@
 
-The following video demonstrates some
-of the features of \tname:
+The following video demonstrates \tname:
 

### 2025-03-21 paper/main.tex
Fixed underline
minor
Removed fix
polishing conclusions

@@
 
+\vspace{-1ex}
 \subsection{Usage}
@@
 follows. First, a Docker container associated with the tool is created using
-\CodeIn{install_freefuzz_docker.sh}. Next, a reproducible bug is tested using
+\CodeIn{install\_freefuzz\_docker.sh}. Next, a reproducible bug is tested using
 the specified library version as input to verify the setup.
@@
 
-\Fix{Abid: Added text to motivate adding support for these APIs, please revise}
+% \Fix{Abid: Added text to motivate adding support for these APIs, please revise}
 
@@
 
-\subsection{Contribution}
+\subsection{Contributions}
 
@@
 barrier to the proper evaluation of these techniques. \tname{} fills
-the gaps. It includes a total of \numbugs\ across three major DL
-libraries. We plan to continue expanding this dataset and to explore
-automated approaches to extract patches from issue trackers and
-``frontport'' them~\cite{hazimeh2020magma} to a single version of the
-library to facilitate testing.
+this gap. It includes a total of \numbugs\ across three major DL
+libraries and provides an infrastructure to integrate fuzzers and
+evaluate them. We plan to continue expanding this dataset and to
+explore automated approaches to extract patches from issue trackers
+and ``frontport'' them~\cite{hazimeh2020magma} to a single version of
+the library to facilitate testing even further.
 

### 2025-04-21 paper/main.tex
minor
Added copyright information

@@
 %% of Software Engineering (FSE '25), June 23--27, 2025, Trondheim, Norway}
-
+\copyrightyear{2025}
+\acmYear{2025}
+\setcopyright{acmlicensed}\acmConference[ISSTA Companion '25]{34th ACM SIGSOFT International Symposium on Software Testing and Analysis}{June 25--28, 2025}{Trondheim, Norway}
+\acmBooktitle{34th ACM SIGSOFT International Symposium on Software Testing and Analysis (ISSTA Companion '25), June 25--28, 2025, Trondheim, Norway}
+\acmDOI{10.1145/3713081.3731739}
+\acmISBN{979-8-4007-1474-0/2025/06}
 %%
@@
 
-The following video demonstrates \tname:
+\vspace{0.5ex}\noindent{}The following video demonstrates \tname:
 
@@
 
-The archived version at Zenodo is available with this DOI:
+\vspace{0.5ex}\noindent{}The archived version at Zenodo is available with this DOI:
 

### 2025-04-21 paper/main.tex
Added acknowledgements

@@
 
-\setcopyright{none} % to remove the copyright notice
-\settopmatter{printacmref=false} % to remove the ACM Reference Format
-\renewcommand\footnotetextcopyrightpermission[1]{} % to remove copyright box
+% \setcopyright{none} % to remove the copyright notice
+% \settopmatter{printacmref=false} % to remove the ACM Reference Format
+% \renewcommand\footnotetextcopyrightpermission[1]{} % to remove copyright box
 
@@
 %% of Software Engineering (FSE '25), June 23--27, 2025, Trondheim, Norway}
+\setcopyright{acmlicensed}
 \copyrightyear{2025}
 \acmYear{2025}
-\setcopyright{acmlicensed}\acmConference[ISSTA Companion '25]{34th ACM SIGSOFT International Symposium on Software Testing and Analysis}{June 25--28, 2025}{Trondheim, Norway}
+\acmDOI{10.1145/3713081.3731739}
+\acmConference[ISSTA Companion '25]{34th ACM SIGSOFT International Symposium on Software Testing and Analysis}{June 25--28, 2025}{Trondheim, Norway}
 \acmBooktitle{34th ACM SIGSOFT International Symposium on Software Testing and Analysis (ISSTA Companion '25), June 25--28, 2025, Trondheim, Norway}
-\acmDOI{10.1145/3713081.3731739}
 \acmISBN{979-8-4007-1474-0/2025/06}
@@
 
+\section{Acknowledgements}
+This work was supported and funded by the National Science Foundation grant numbers CCF-2349961.
+
 \balance

### 2025-04-21 paper/main.tex
Fixed table 1, fixed author name, removed page number
small changes

@@
 
-\author{M. M. Abid Naziri}
+\author{M M Abid Naziri}
 \affiliation{%
@@
 %% add page numbers
-\pagestyle{plain}
+% \pagestyle{plain}
 
@@
   \centering
+  \small
   \caption{\label{table:bug-characterization}Characterization of
-    reproducible bugs from \tname.}
+    bugs from \tname.}
+  \vspace{-1ex}
   %%   \Fix{Is this up to date? I have seen
@@
   \\ \cmidrule(lr){2-4} \jax{} & 46 & 45-1 & 45-1 \\ \torch{} & 37 &
-  18-19 & 21-16 \\ \tf{} & 24 & 23-1 & 24-0 \\ \midrule
-  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 86-21& 90-17
+  18-19 & 21-16 \\ \tf{} & 29 & 27-2 & 29-0 \\ \midrule
+  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 90-22& 95-17
   \\ \bottomrule
   \end{tabular}
+  \vspace{-2ex}  
 \end{table}
@@
 \begin{table}
+  \small
   \centering
@@
     from \tname.}
+  \vspace{-1ex}
   \begin{tabular}{lrrrrr}\toprule
@@
   \end{tabular}
+  \vspace{-2ex}  
 \end{table}
@@
 \begin{table}
+  \small
   \centering
-  \caption{\label{table:bug-interface}\tname's bug interface.}
+  \caption{\label{table:bug-interface}\tname command-line interface.}
+  \vspace{-1ex}
 \begin{tabular}{lp{6.5cm}}
@@
 \end{tabular}
+  \vspace{-3ex}
 \end{table}
@@
 
-Let us use the bug 120903~\cite{torch120903} from \torch\ to demonstrate the
+Let us use bug 120903~\cite{torch120903} from \torch\ to demonstrate the
 command \CodeIn{run-test}, which runs a test to reproduce a bug on an
-environment with the necessary dependencies installed. Use the
+environment with needed dependencies installed. Use the
 following command to reproduce the bug:
@@
 The
-directory \CodeIn{tool-integration} that contains templates for these
+directory \CodeIn{tool-integration} contains templates for these
 scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
@@
 % \Fix{up to here}
-
 We demonstrate the integration of FreeFuzz~\cite{wei2022free}. The
-following script creates a Docker container associated with FreeFuzz.
+following script creates a Docker container for FreeFuzz.
 
@@
 \section{Conclusion and Future Work}
-Deep Learning (DL) Libraries (e.g., \torch) provide the basic blocks
-for creating AI-enabled applications, which are becoming very
-popular. Several testing techniques have been proposed in the
-literature to find bugs in these libraries. Unfortunately, the lack of
-a dataset of reproducible bugs in those libraries poses an important
-barrier to the proper evaluation of these techniques. \tname{} fills
-this gap. It includes a total of \numbugs\ across three major DL
-libraries and provides an infrastructure to integrate fuzzers and
-evaluate them. We plan to continue expanding this dataset and to
-explore automated approaches to extract patches from issue trackers
-and ``frontport'' them~\cite{hazimeh2020magma} to a single version of
-the library to facilitate testing even further.
+Deep Learning Libraries provide the basic blocks for creating
+AI-enabled applications. Several testing techniques have been proposed
+in the literature to find bugs in these libraries. Unfortunately, the
+lack of a dataset of reproducible bugs in those libraries poses an
+important barrier to the proper evaluation of these
+techniques. \tname{} fills this gap. It includes a total of
+\numbugs\ bugs across three major DL libraries and provides an
+infrastructure to evaluate fuzzers.  To facilitate evaluation of
+testing techniques even further we plan to continue expanding this
+dataset and to explore automated approaches to ``frontport'' bugs into
+single version of the library as in the Magma
+benchmark~\cite{hazimeh2020magma}.
 
-\section{Acknowledgements}
+\section*{Acknowledgements}
 This work was supported and funded by the National Science Foundation grant numbers CCF-2349961.

### 2025-04-24 paper/main.tex
Refined some sentences according to reviews

@@
 environment to reproduce the bug (venv or docker). Co-incidentally,
-all bugs that require a GPU build are reproduced using a docker
-container, i.e. the column venv-docker matches would have been
-observed with a column CPU-GPU, to indicate if the bug is can be
+all bugs that require a GPU are reproduced using docker
+containers, i.e. the column venv-docker matches what would have been
+observed with a column CPU-GPU, to indicate if the bug can be
 reproduced with a CPU or if it requires a
@@
 
-The following script runs FreeFuzz all bugs associated with version
+The following script runs FreeFuzz on all bugs associated with version
 2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
@@
 script containing the commands to run the tool
-(\CodeIn{run\_freefuzz\_docker.sh}. The script reports on output how
-many bugs are reproducible with this library version were successfully
+(\CodeIn{run\_freefuzz\_docker.sh}. The script reports how
+many bugs that are reproducible with this version of the library were successfully
 reproduced by the given tool.  Tool execution proceeds as

### 2025-04-24 paper/main.tex
Explained why specific bugs were selected and why other issues/bugs are not reproducible, shortened code snippet for space

@@
 %
-Finally, we assess the reproducibility of the bug by creating a
+Finally, we do a deeper analysis on these bugs. We find some bugs that
+are related to building/installation/problematic unit tests instead of
+bugs in the core API functionality, as well as some bugs that lack any
+code snippet provided with the bug report to reproduce the bug. These
+bugs can be detected and discarded at this stage.
+We assess the reproducibility of a bug by creating a
 virtual environment that contains the necessary dependencies to
-reproduce the bug.  Once we can successfully reproduce the bug by
-creating the enviroment detailed in the report, we include the
+reproduce the bug. Some bugs require very specific hardware (e.g. TPU) 
+or can not be reproduced due to an expired nightly build that can no
+longer be accessed. We successfully reproduce the bug if none of these
+issues are present by
+creating the enviroment detailed in the report, and we include the
 corresponding artifacts in our dataset. Throughout this process, we
@@
 \begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
-$> run-tool --container freefuzz --library-name pytorch \ 
-   --use-library-version 2.2.0 \
+$> run-tool -c freefuzz -l pytorch -v 2.2.0 \
    --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
@@
 The output looks like the following:
-
 \begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
@@
 ...
-====== test session starts ======
-platform linux -- Python 3.10.0, pytest-8.2.0, pluggy-1.5.0
-...
-RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please report a bug to PyTorch.
+RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL 
+ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please
+report a bug to PyTorch.
 ====== 1 passed in 1.09s ======
-...
 Updating environment in the container of the testing tool
-Successfully copied 16.4kB to freefuzz:/tmp/issue_120903
 ...

### 2025-04-24 paper/main.tex
Updated spacing, fixed some text

@@
 requests linked to them. We then create a filter that incorporates
-the periods mentioned above, the label, the issue status being closed
+the periods mentioned above, the label (bug), the issue status being closed
 and the presence of a linked pull request. We found \numtorchfiltered{}
@@
 reproduce the bug, dependencies required for the bug reproduction,
-clear description of the desired behavior, etc. We discard bugs that
+clear description of the desired behavior, etc. We discard cases that
 are not in the core functionality of the library e.g. documentation
@@
 %
-Finally, we do a deeper analysis on these bugs. We find some bugs that
+Finally, we do a deeper analysis on these bugs. We find some cases that
 are related to building/installation/problematic unit tests instead of
@@
 creating the enviroment detailed in the report, and we include the
-corresponding artifacts in our dataset. Throughout this process, we
+corresponding artifacts in our dataset. We use a virtual enviroment
+(conda~\cite{venv}) when the bug can be reproduced on a CPU, and we use docker
+containers~\cite{merkel2014docker} with appropriate CUDA drivers when the bug 
+requires a GPU.
+Throughout this process, we
 obtain \textbf{\numjaxbugs{}}, \textbf{\numtorchbugs{}}, and
@@
 
+\vspace{-1ex}
 \subsection{Challenges}
@@
 \label{sec:method}
-
 The following steps show the method we use to create bug instances:
-
+\vspace{-5mm}
 \begin{enumerate}[leftmargin=0.5cm]
@@
 \end{enumerate}
-
 \textbf{Test Oracles.}~
@@
   The issue no. 120903 in \torch\ has the following test code that checks the oracle:
-
+\vspace{-1ex}
 \begin{lstlisting}[language=python,basicstyle=\small,]
@@
 \end{lstlisting}
-
+\vspace{-1ex}
 In this example, the unexpected behavior is a \CodeIn{RuntimeError} thrown by the call to the \CodeIn{fake\_quantize\_per\_channel\_affine} API from \torch.
@@
 
+\vspace{-1ex}
 \section{\tname} % : Database of Bugs in DL libraries
@@
 
+\vspace{-1ex}
 \subsection{Contributions}
@@
 
+\vspace{-1ex}
 \section{Related Work}
@@
 % Denchmark~\cite{kim2021denchmark}
-
+\vspace{-1ex}
 \section{Conclusion and Future Work}

### 2025-04-24 paper/main.tex
minor changes to fit text in 4 pages

@@
 
-\vspace{0.5ex}\noindent{}The following video demonstrates \tname:
+\vspace{0.5ex}\noindent{}The video from this URL demonstrates \tname:
 
@@
 run-tool & Runs a testing tool in a given buggy environment \\
-show-info & Shows information about the tests available on this benchmark\\
+show-info & Shows information about available tests\\
 stats & Shows statistics about this dataset (e.g., number of tests
-that require GPU, number of tests that reproduce bugs in C or Python
-code, etc.)\\
+that require GPU, etc)\\
+%% number of tests that reproduce bugs in C or Python
+%% code, etc.)\\
 \bottomrule
@@
 \begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
-Using bug-id 120903 for library pytorch version 2.2.0
-...
+Using bug-id 120903 for library pytorch version 2.2.0...
 RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL 
@@
 ====== 1 passed in 1.09s ======
-Updating environment in the container of the testing tool
-...
+Updating environment in the container of the testing tool...
 Running the testing tool on the environment of the bug
@@
 Testing on  ['torch']
-torch.atanh
-...
+torch.atanh...
 No violation of precision-oracle in the compare-bug category

### 2025-04-24 paper/main.tex
Updated venv to conda

@@
   \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
-  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
+  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & conda-docker
   \\ \cmidrule(lr){2-4} \jax{} & 46 & 45-1 & 45-1 \\ \torch{} & 37 &
@@
 ``environment'' shows the breakdown of instances for each kind of
-environment to reproduce the bug (venv or docker). Co-incidentally,
+environment to reproduce the bug (conda enviroment or docker). Co-incidentally,
 all bugs that require a GPU are reproduced using docker
-containers, i.e. the column venv-docker matches what would have been
+containers, i.e. the column conda-docker matches what would have been
 observed with a column CPU-GPU, to indicate if the bug can be

### 2025-04-25 paper/main.tex
Updated run-tool example to include an API supported by FreeFuzz

@@
 The following script runs FreeFuzz on all bugs associated with version
-2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
+2.2.1+cu121 of \torch.  The command \CodeIn{run-tool} takes the library
 version as an input, along with the name of the docker container
@@
 \begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
-$> run-tool -c freefuzz -l pytorch -v 2.2.0 \
+$> run-tool -c freefuzz -l pytorch -v 2.2.1+cu121 \
    --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
@@
 \begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
-Using bug-id 120903 for library pytorch version 2.2.0...
-RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL 
-ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please
-report a bug to PyTorch.
-====== 1 passed in 1.09s ======
-Updating environment in the container of the testing tool...
+Using bug-id 121725 for library pytorch version 2.2.1+cu121
+...
+RuntimeError: Please look up dimensions by name, got: name = None.
+====== 1 passed in 0.63s ======
+Updating environment in the container of the testing tool
+...
 Running the testing tool on the environment of the bug
 APIs under test:
-torch.fake_quantize_per_channel_affine
-torch.all
-torch.compile
+torch.logsumexp
+torch.autograd.grad
 Testing on  ['torch']
-torch.atanh...
+torch.multinomial
+...
 No violation of precision-oracle in the compare-bug category
@@
 No violation of crash-oracle in the potential-bug category
--> torch.fake_quantize_per_channel_affine did not face any failures
--> torch.all did not face any failures
--> torch.compile did not face any failures
-Reproduced 0 out of 3 bugs
+-> torch.logsumexp did not face any failures
+-> torch.autograd.grad did not face any failures
+Reproduced 0 out of 2 bugs
 \end{lstlisting}
@@
 The execution log shows that the tool did not reproduce any of the
-three bugs that were expected to be reproduced since the three buggy APIs \CodeIn{torch.fake\_quantize\_per\_channel\_affine}, \CodeIn{torch.all}, and \CodeIn{torch.compile} are not supported by FreeFuzz.
-The outputs of the tool are saved in the container and can be inspected manually to further inspect the execution log.
-From this result, the developer can decide to add support for these three APIs in FreeFuzz and run the tool again to check if the bugs can be reproduced now.
-This will allow developers to decide on which APIs to add support for.
+two bugs that were expected to be reproduced. 
+% since the three buggy APIs \CodeIn{torch.fake\_quantize\_per\_channel\_affine}, \CodeIn{torch.all}, and \CodeIn{torch.compile} are not supported by FreeFuzz. 
+Among the two buggy APIs, FreeFuzz supports \CodeIn{torch.logsumexp} but the bug could not be reproduced, whereas FreeFuzz does not support \CodeIn{torch.autograd.grad}.
+The outputs from the tool are saved in the container so that the execution log can be inspected further manually.
+% can be inspected manually to further inspect the execution log. 
+From this result, the developer can debug and refine their technique to catch bugs that it missed, as well as add support for APIs that are currently unsupported.
 

### 2025-04-25 paper/main.tex
Profread and made minor changes

@@
 of reproducible bugs to evaluate their effectiveness. The lack of an
-evaluation standards is a serious obstacle to a fair and rigorous
+evaluation standard is a serious obstacle to a fair and rigorous
 comparison of techniques and hinders research progress.
@@
 \begin{enumerate}[leftmargin=0.2in]
-\item developers should be able to write tests scripts in Python;
-\item ~they should be able to handle nighly builds and specific
+\item developers should be able to write test scripts in Python;
+\item they should be able to handle nighly builds and specific
   versions of CUDA (\textsection~\ref{sec:challenges});
@@
 reproduced with a CPU or if it requires a
-GPU. Table~\ref{table:bug-stats} shows the breakdown error types for
+GPU. Table~\ref{table:bug-stats} shows the breakdown of error types for
 the bugs in our dataset. The row ``Incorrect Output'' is listed first
 as it requires a distinct kind of oracle comparing consistency of the
-outputs of test runs on a CPU and on GPU. In total, we have
+outputs of test runs on a CPU and on a GPU. In total, we have
 \numbugtypes\ different types of bug manifestations across the three
@@
 are related to building/installation/problematic unit tests instead of
-bugs in the core API functionality, as well as some bugs that lack any
-code snippet provided with the bug report to reproduce the bug. These
+bugs in the core API functionality, as well as some cases that are simply API misuses, not bugs. These
 bugs can be detected and discarded at this stage.
@@
 reproduce the bug. Some bugs require very specific hardware (e.g. TPU) 
-or can not be reproduced due to an expired nightly build that can no
-longer be accessed. We successfully reproduce the bug if none of these
+or can not be reproduced due to requiring a debug build that only the developers can access. We successfully reproduce the bug if none of these
 issues are present by
@@
 require specific CUDA drivers to be installed on the system. Python
-virtual enviroments are not designed to enable change of OS drivers.
+virtual environments are not designed to enable changing OS drivers.
 % GPU builds\Fix{I don't understance GPU builds. do you mean
@@
   \item Write a script that creates the virtual environment (either
-    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
+    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container~\cite{merkel2014docker}) and runs
     the test on it;
   \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
-    artifacts mentioned above, where \CodeIn{lib} refers to the
-    affected library and \CodeIn{bug-id} is a fresh identifier of the
-    bug instance.
+    artifacts mentioned above, where \CodeIn{lib} is the
+    affected library and \CodeIn{bug-id} is the issue number of the bug report.
+    % is a fresh identifier of the
+    % bug instance.
     %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
@@
 specific library version (\CodeIn{preprocess.py}), and (3) a postprocessing script to match the
-execution log with the expected errors (\CodeIn{postprocess.py}) needs to be provided.
+execution log with the expected errors (\CodeIn{postprocess.py}).
 % \Fix{name
@@
 \noindent
-The script \CodeIn{install\_freefuzz\_docker.sh} build the docker
+The script \CodeIn{install\_freefuzz\_docker.sh} builds the docker
 container that encapsulates FreeFuzz.
@@
 script containing the commands to run the tool
-(\CodeIn{run\_freefuzz\_docker.sh}. The script reports how
+(\CodeIn{run\_freefuzz\_docker.sh}). The script reports how
 many bugs that are reproducible with this version of the library were successfully

### 2025-05-12 paper/main.tex
Added affiliation city and ccs, adjusted space

@@
 \affiliation{%
-  \institution{NC State University, USA}
-  %\city{Rocquencourt}
+  \institution{NC State University, Raleigh, USA}
+  % \city{Raleigh}
+  % \country{USA}
   \country{}
@@
 \affiliation{%
- \institution{Amrita Vishwa Vidyapeetham, India}
- %% \city{Doimukh}
- %% \state{Arunachal Pradesh}
+ \institution{Amrita Vishwa Vidyapeetham, Coimbatore, India}
+%  \city{Coimbatore}
+%  \country{India}
  \country{}
@@
 \affiliation{%
- \institution{NC State University, USA}
- %% \city{Doimukh}
- %% \state{Arunachal Pradesh}
+\institution{NC State University, Raleigh, USA}
+% \city{Raleigh}
+% \country{USA}
 \country{}
@@
 \affiliation{%
- \institution{Purdue University, USA}
- %% \city{Doimukh}
- %% \state{Arunachal Pradesh}
+ \institution{Purdue University, West Lafayette, USA}
+%  \city{West Lafayette}
+%  \country{USA}
  \country{}
@@
 \affiliation{%
- \institution{Cornell University, USA}
- %% \city{Doimukh}
- %% \state{Arunachal Pradesh}
+ \institution{Cornell University, Ithaca, USA}
+%  \city{Ithaca}
+%  \country{USA}
  \country{}
@@
 %% \end{CCSXML}
+\vspace{-0.3cm}
+\begin{CCSXML}
+  <ccs2012>
+    <concept>
+        <concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
+        <concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
+        <concept_significance>500</concept_significance>
+        </concept>
+  </ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Software and its engineering~Software testing and debugging}
 
@@
 %% the work being presented. Separate the keywords with commas.
+\vspace{-0.3cm}
 \keywords{Deep learning libraries, testing, benchmarking}
@@
 
+\vspace{-2ex}
 \section{Introduction}
@@
 criteria:
-
-\begin{enumerate}[leftmargin=0.2in]
-\item developers should be able to write test scripts in Python;
-\item they should be able to handle nighly builds and specific
-  versions of CUDA (\textsection~\ref{sec:challenges});
-\item they should be able to integrate fuzzing tools in the framework.
+% \vspace{-2ex}
+\begin{enumerate}[leftmargin=0.2in,topsep=0pt]
+\item ability to write test scripts in Python;
+\item handlin nightly builds and specific
+  CUDA versions (\textsection~\ref{sec:challenges});
+\item ability to integrate fuzzing tools in the framework.
 \end{enumerate}  
-
+% \vspace{-2ex}
 Note that DL libraries are written in Python. Existing datasets of
@@
 %\Fix{Need to add text regarding differentiating the tool from BugsInPy}
-
+\vspace{-0.29cm}
 \section{Tool Availability}
@@
 \tname\ is publicly available from the following URL:
-
 \url{https://github.com/ncsu-swat/bugsindlls}
 
-\vspace{0.5ex}\noindent{}The video from this URL demonstrates \tname:
-
+\noindent{}The video from this URL demonstrates \tname:
 \url{https://www.youtube.com/watch?v=NslNWrULT1c}
 
-\vspace{0.5ex}\noindent{}The archived version at Zenodo is available with this DOI:
+% \vspace{0.5ex}\noindent{}The archived version at Zenodo is available with this DOI:
 
-\url{https://doi.org/10.5281/zenodo.15064163}\\
+% \url{https://doi.org/10.5281/zenodo.15064163}\\
 
@@
 % the tool at zenodo}
-
+\vspace{-0.2cm}
 \section{Objects and Methods}
@@
 
+\vspace{-1ex}
 \section*{Acknowledgements}
